---
title: "Data Cleaning: ‘yourPersonality‘ data"
author: "[blinded]" 
toc: true
toc-depth: 6
toc-title: Contents
number-sections: true
execute:
  cache: false
format:
#  docx:
#    highlight-style: github
  html:
    link-external-icon: true
    link-external-newwindow: true
    code-block-bg: true
    code-block-border-left: "#31BAE9"
    embed-resources: true
#comments:
#  hypothesis: true
editor: source
bibliography: 
#  - document_citations.bib
  - grateful-refs.bib
csl: apa.csl
---

# Preparations 

## Load packages

```{r}
#| echo: true
#| warning: false
#| code-fold: true
#| code-summary: "Show the code"
#| cache: false

library(tidyverse)
library(labelled)
library(psych)
library(lavaan)
library(grateful)
library(knitr)
```

# Data cleaning

## Load data

1) Long file containing all weeks of survey data from the YourPersonality data (exploratory N=300 partial data set)  

2) Long file containing all weeks of survey data from the YourPersonality data (remaining data, often used for confirmatory analyses )  

Here, we combine both data sets.  

```{r load}
#| echo: true
#| warning: false
#| output: true
#| cache: false

df_expl <- read.delim("data/raw/explore2long.txt") %>% arrange(user_id, time) %>% as_tibble()
df_conf <- read.delim("data/raw/confirm2long.txt") %>% arrange(user_id, time) %>% as_tibble()
```

## Combine and clean

Combine both data sets 
```{r combine}
#| echo: true
#| warning: false
#| output: true
#| cache: false

# check IDs first
df_expl %>% summarise(n_distinct(user_id))
summary(df_expl$user_id)

df_conf %>% summarise(n_distinct(user_id))
summary(df_conf$user_id)

# combine
df_atta_full <- bind_rows(df_expl, df_conf) %>% arrange(user_id, time)
rm(df_conf)
rm(df_expl)

df_atta_full %>% summarise(n_distinct(user_id))
summary(df_atta_full$user_id)
```

Select relevant variables: 
```{r select}
#| echo: true
#| warning: false
#| output: true
#| cache: false

df_atta <- df_atta_full %>% 
  group_by(user_id) %>% # create custom ID
  mutate(pid = cur_group_id()) %>% 
  ungroup() %>% 
  mutate(year = as.numeric(substr(registration_date, 1, 4))) %>% 
  select(pid, time, sex, birthyear, year, 
         # country, ethnicity,  # -> almost all from US; ethniticy was open response, therefore not really helpful
         # from background information - assessed in the beginning and could be changed manually afterwards: 
         education, religion, politics, libcon, involved, involved2, employed, 
         starts_with(c("avoid", "anxiety")), # attachment variables (a-e)
         swb, # life satisfaction
         event_dating = event08, event_engage = event12, 
         event_marrie = event13, event_separa = event22, event_divorc = event23, 
         submission_date3_365, submission_date4_365)

# randomly selected example of data structure:
df_atta %>%
  semi_join(
    df_atta %>%
      distinct(pid) %>%
      slice_sample(n = 1),
    by = "pid"
  ) %>% select(time, submission_date3_365, involved, event_dating, event_separa, avoide, anxietye) %>% print(n=30)

# no time gaps in between (skipped asssessments) are considered; 'time‘ just fills up from 0 up to 23 in the order of completed surveys    
```

### Filter data

Filter to valid responses (broadly) 

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

# only keep actual answered waves (other rows are all NA)
df_atta <- df_atta %>% 
  filter(!is.na(submission_date3_365))

# number of waves per person
df_atta %>%
    count(pid) %>%
    summarise(mean_n = mean(n), median_n = median(n),
              min_n = min(n), max_n = max(n))

# example case:
df_atta %>% 
  filter(pid==666) %>% 
  select(time, submission_date3_365, involved, event_dating, event_separa, avoide, anxietye) %>% print(n=30)
# 'time' is not very useful because it just counts the assessments per person and does not consider skipped waves
```

Filter to participants with sufficient longitudinal information  

We preregistered: "Altogether, we require at least 3 consecutively answered survey waves for each participant to be considered in either group."  

The tricky thing is "consecutively answered" because the waves are not spaced with the same time gaps. We approximate this: everything with up to 2 months of time in between waves can be considered consecutive.  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

# code months
df_atta <- df_atta %>% 
  rename(particip_nr = time) %>% 
  mutate(time_years = submission_date3_365) %>% 
  mutate(time_months = submission_date3_365 * 12,
         time_month_rd = round(submission_date3_365 * 12))

# Life events were asked with regard to time since the last assessment: "Participants were asked whether 25 life events or experiences had taken place since the last assessment."

# code as consecutive if monthly lag is less than 3 months 
# or rather be more liberal = 4 or 5 months? (4 would result in ~300 more participants and 5 in another ~200 more; however, these have more pronounced gaps in assessment schedules... I'll stick with 2 months)
df_atta <- df_atta %>% 
  arrange(pid, time_months) %>% 
  group_by(pid) %>% 
  mutate(month_lag = time_months - lag(time_months)) %>% 
  mutate(consec = ifelse(month_lag < 3 | (time_months==0 & lead(month_lag)<3), 1, 0)) %>% 
  ungroup()

# keep cases with 3 consecutive waves:
# A participant qualifies if there is a sequence of 3 assessments where the two gaps between them are each < 3 months.

df_atta <- df_atta %>% 
  group_by(pid) %>% 
  mutate(three_consec = consec & lag(consec) & lag(consec, n=2)) %>% 
  ungroup()

# example of included pid:
df_atta %>% 
  filter(pid==91) %>% 
  select(pid, particip_nr, time_years, time_months, month_lag, consec, three_consec)

# example of excluded pid:
df_atta %>% 
  filter(pid==1580) %>% 
  select(pid, particip_nr, time_years, time_months, month_lag, consec, three_consec)

# extract eligible pid's
eligible_pid <- df_atta %>% 
  filter(three_consec==TRUE) %>% 
  pull(pid) %>% unique()

# filter data to these cases:
df_atta <- df_atta %>% 
  filter(pid %in% eligible_pid)

df_atta %>% summarise(n(), n_distinct(pid))

# check again: number of waves per person
df_atta %>%
    count(pid) %>%
    summarise(mean_n = mean(n), median_n = median(n),
              min_n = min(n), max_n = max(n))
```

### Form groups

1st: consistently single people
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

# Prereg: "For someone to be included in the group of consistently single people, they need to have consistently answered the relationship status question with “No” and also not have selected any of the relationship life events mentioned above."

df_atta %>% filter(is.na(involved2)) %>% summarise(n(), n_distinct(pid)) # drop these participants altogether

df_atta <- df_atta %>% 
  filter(!pid %in% (df_atta %>% filter(is.na(involved2)) %>% pull(pid) %>% unique()))

# sum up all rel. status info per person (has to be all 0!) / then divide by number of waves
df_atta <- df_atta %>% 
  group_by(pid) %>% 
  mutate(prop_rel = sum(involved2) / n()) %>% 
  ungroup()

# These are the events we consider - all have to stay 0 throughout!
df_atta %>% filter(prop_rel==0 & pid==27) %>% 
  select(pid, time_months, starts_with("event")) %>% print(n=20) # example case who dated casually

df_atta <- df_atta %>% 
  group_by(pid) %>% 
  mutate(sum_events = sum(event_dating + event_engage + event_marrie + event_separa + event_divorc)) %>% 
  ungroup()

df_atta <- df_atta %>% 
  mutate(single_consist = ifelse(prop_rel==0 & sum_events==0, 1, 0))

df_atta %>% filter(single_consist==1) %>% summarise(n = n(), N=n_distinct(pid))
```

2nd: consistently partnered people
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

# Prereg: "For someone to be included in the group of consistently partnered individuals, they need to have consistently answered the relationship status question with either “Yes, I am dating someone”, or “Yes, I am married”, while also never selecting the events indication new relationship formation, break-up, or divorce."

# These are the events we consider - all have to stay 0 throughout!
df_atta %>% filter(prop_rel==1 & pid==18) %>% 
  select(pid, time_months, event_dating, event_separa, event_divorc) %>% print(n=20) # example case

df_atta <- df_atta %>% 
  group_by(pid) %>% 
  mutate(sum_events_3 = sum(if_else(row_number() == 1, 0L, event_dating) + # starting dating in the first wave is allowed
                              event_separa + event_divorc)) %>% 
  ungroup()

df_atta <- df_atta %>% 
  mutate(partner_consist = ifelse(prop_rel==1 & sum_events_3==0, 1, 0))

df_atta %>% filter(partner_consist==1) %>% summarise(n = n(), N=n_distinct(pid))
```

3rd: intermittently partnered people
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

# Prereg: "Finally, for someone to be included in the group of intermittently partnered individuals, they need to have answered the relationship status question with “Yes, I am dating someone”, or “Yes, I am married” at least once and with “No” at least once. No additional conditions due to life events are applied."

df_atta <- df_atta %>% 
  mutate(partner_interm = ifelse(prop_rel>0 & prop_rel<1, 1, 0))

df_atta %>% filter(partner_interm==1) %>% summarise(n = n(), N=n_distinct(pid))
# slightly higher number of waves per person here
```

Last, we also need another group for the selection effects (RQ1): "... with consistent singlehood (0 = no, initially single but later find partner, 1 = yes, consistently single) as the outcome"

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

# single at baseline but later find a partner
# first: single at baseline
df_atta <- df_atta %>% 
  mutate(single_w1 = ifelse(particip_nr==0 & involved2==0, 1, 0)) %>% 
  group_by(pid) %>% 
  mutate(single_w1_max = max(single_w1)) %>% 
  ungroup()

# second: combine with prop_rel
df_atta <- df_atta %>% 
  mutate(single_later_partn = ifelse(single_w1_max==1 & prop_rel>0, 1, 0))

# below, we combine these to form a distinct analysis df for RQ1
# - consistently single & initially single, later partnered
```

Now filter to include only those who are in one of the three (plus 1) groups: 
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

df_atta %>% summarise(n = n(), N=n_distinct(pid))

df_atta <- df_atta %>% 
  filter(single_consist==1 | partner_consist==1 | partner_interm==1 | single_later_partn==1)
# the cases that are dropped could not be clearly categorized (e.g., always involved==1 but still reporting events)
df_atta %>% summarise(n = n(), N=n_distinct(pid))
```

### Code time

A few descriptive numbers first: 
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

# distribution of max_month (time from registration to last assessment):
df_atta %>%
    group_by(pid) %>%
    summarise(
        n_assessments = n(),
        max_month = max(submission_date3_365 * 12)
    ) %>%
    summarise(
        mean_max = mean(max_month),
        median_max = median(max_month),
        q90 = quantile(max_month, .90),
        q95 = quantile(max_month, .95),
        max = max(max_month)
    )
# Half of participants finish their available assessments by ~16 months. 10% extend beyond ~31 months. A small but non-negligible group extends to ~3–3.5 years.

# Calculate the relationship between: number of assessments completed & maximum follow-up time
df_atta %>%
    group_by(pid) %>%
    summarise(
        n_assessments = n(),
        max_month = max(submission_date3_365 * 12)
    ) %>%
    cor() # 0.76 is the relevant cor -> people with more assessments tend to be observed over longer periods

# describe extent of deviations through rounding:
df_atta %>%
  mutate(rounding_error = time_months - time_month_rd,
         abs_rounding_error = abs(rounding_error)) %>%
  summarise(
    mean_abs_error = mean(abs_rounding_error, na.rm = TRUE),
    median_abs_error = median(abs_rounding_error, na.rm = TRUE),
    q95_abs_error = quantile(abs_rounding_error, 0.95, na.rm = TRUE),
    max_abs_error = max(abs_rounding_error, na.rm = TRUE)
  )
# mostly around 0.2 months (~6 days)

df_atta %>% count(time_month_rd) %>% print(n=50)
# may be good to use a monthly grid up to ~32–35 months and discard later months

# Another issue: the rounding creates duplicate person-months. This cannot be handled when transforming to wide format.
```

For now we try with 35 months as the upper limit:
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

df_atta <- df_atta %>% 
  filter(time_month_rd<=35)
# This drops 191 obs 107 from pers
df_atta %>% summarise(n = n(), N=n_distinct(pid))

df_atta %>% count(time_month_rd) %>% print(n=50)
```

Deal with duplicate person-months (in the rounded month variable):
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

# get some information first
df_atta %>%
  count(pid, time_month_rd) %>%
  filter(n > 1) %>%
  summarise(
    n_duplicate_cells = n(),
    n_people = n_distinct(pid),
    max_duplicates = max(n)
  )
# only 1.6% extra observations due to duplicate person-months

df_atta %>%
  group_by(pid, time_month_rd) %>%
  filter(n() > 1) %>%
  summarise(
    min_time = min(time_months),
    max_time = max(time_months),
    spread = max_time - min_time,
    n = n(),
    .groups = "drop"
  ) %>%
  summarise(
    median_spread = median(spread),
    q95 = quantile(spread, .95),
    max_spread = max(spread)
  )
# spread = max(time_months) - min(time_months)
# Median spread = ~3 days
# 95th percentile	~22 days
# Maximum	~30 days

# this participant should be dropped altogether (must be a more serious error):
df_atta %>% 
  filter(pid==97) %>% 
  select(pid, particip_nr, time_years, time_months, time_month_rd, avoide, anxietye) %>% print(n=100)
df_atta <- df_atta %>% 
  filter(pid!=97)

# With the other cases, I will first attempt a repair / correction function to "save" some cases where the earlier rounding artificially caused duplicate months. Second, I will drop any remaining duplicate person-months, keeping only the first entry per person-month.

# Step 1: Create a copy of the rounded month variable
df_atta <- df_atta %>%
  mutate(time_month_rd_corrected = time_month_rd)
# Step 2: Identify duplicate person-month combinations
duplicates_month <- df_atta %>%
  count(pid, time_month_rd) %>%
  filter(n > 1)
# Step 3: Add the duplicate information back to the data
df_atta <- df_atta %>%
  left_join(
    duplicates_month %>% 
      select(pid, time_month_rd, n),
    by = c("pid", "time_month_rd")
  ) %>%
  rename(n_same_month = n)

# Step 4: Calculate exact-time gaps within duplicated months
# For each duplicate month, order observations by their actual time:
df_atta <- df_atta %>%
  group_by(pid, time_month_rd) %>%
  arrange(time_months, .by_group = TRUE) %>%
  mutate(
    duplicate_order = if_else(
      n_same_month > 1,
      row_number(),
      NA_integer_),
    duplicate_gap = if_else(
      n_same_month > 1,
      time_months - lag(time_months),
      NA_real_)) %>%
  ungroup()

# Step 5: Identify repair candidates
# rules: duplicated month; second observation in that month; exact gap ≥ 3/5 month; next month is currently "empty"
df_atta <- df_atta %>% # First create a variable for the possible shifted month
  mutate(proposed_month = time_month_rd + 1)

occupied_months <- df_atta %>% # Then check whether that month already exists for that person
  select(pid, time_month_rd) %>%
  distinct() %>%
  mutate(month_exists = TRUE)

df_atta <- df_atta %>%
  left_join(occupied_months %>%
      rename(proposed_month = time_month_rd,
             proposed_exists = month_exists),
      by = c("pid", "proposed_month"))

# Step 6: Flag observations that can be shifted
df_atta <- df_atta %>%
  mutate(repair_duplicate = n_same_month > 1 & duplicate_order == 2 &
           duplicate_gap >= (3/5) & # pretty arbitrary but this seems reasonable
           is.na(proposed_exists),
         TRUE, FALSE)
table(df_atta$repair_duplicate) # this only concerns 25 observations

# Inspect cases: 
df_atta %>%
  filter(repair_duplicate) %>%
  select(pid, particip_nr, time_months, time_month_rd, proposed_month, duplicate_gap) %>% print(n=50)

# Step 7: Apply the correction
# Only now modify the corrected variable:
df_atta <- df_atta %>%
  mutate(time_month_rd_corrected = if_else(repair_duplicate %in% TRUE,
                                           proposed_month,
                                           time_month_rd))

# Drop variables:
df_atta <- df_atta %>%
  select(-time_month_rd) %>%
  rename(time_month_rd = time_month_rd_corrected) %>% 
  select(-n_same_month, -duplicate_order, -duplicate_gap, -proposed_month, -proposed_exists, 
         -repair_duplicate, -"TRUE", -"FALSE")

# Quantify remaining duplicate person-months: 
df_atta %>%
  count(pid, time_month_rd) %>%
  filter(n > 1) %>%
  summarise(
    duplicate_cells = n(),
    participants = n_distinct(pid)
  )

# distance 
df_atta %>%
    group_by(pid, time_month_rd) %>%
    summarise(
        spread = max(time_months) - min(time_months),
        n = n(),
        .groups = "drop"
    ) %>%
    summarise(
        median_spread = median(spread),
        q95_spread = quantile(spread, .95),
        max_spread = max(spread)
    )
# most of these duplicates are filled out on the same day
```

Drop the remaining duplicate person-months: 
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

df_atta %>% summarise(n = n(), N = n_distinct(pid))
  
df_atta <- df_atta %>%
  arrange(pid, time_months) %>%
  group_by(pid, time_month_rd) %>%
  slice_head(n=1) %>%
  ungroup()

df_atta %>% summarise(n = n(), N = n_distinct(pid))
# 589 duplicate assessments dropped

table(df_atta$time_month_rd, useNA = "always")
```

## Code demographic variables

Gender: 

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

df_atta %>% group_by(sex) %>% tally()

df_atta <- df_atta %>% 
  mutate(woman = if_else(sex=="0", 1, 0, NA_real_),
         man = if_else(sex=="1", 1, 0, NA_real_))
```

Age:

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false
#| width: 5
#| height: 5

df_atta %>% group_by(pid) %>%
  slice_head(n=1) %>%
  ungroup() %>% pull(birthyear) %>% hist()

df_atta <- df_atta %>% 
  mutate(age = ifelse(!is.na(birthyear), year-birthyear, NA))

df_atta %>% filter(is.na(age)) %>% select(1:5, age, sex) 
# partly missing demographic information for 3 participants

# also code age at baseline
df_atta <- df_atta %>% 
  mutate(age_base = ifelse(particip_nr==0, age, NA))

df_atta <- df_atta %>% 
  fill(age_base, .direction = "downup", .by = pid)

df_atta %>% select(1:5, age, sex, age_base) %>% filter(age!=age_base) 
# these are the same; not really necessary (likely that 'year' just refers to the baseline) -> but ok for us!
```

# RQ1: selection effects data frame

## Filter and collapse to cross-sectional

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

df_atta_rq1 <- df_atta %>%
  filter(single_consist==1 | single_later_partn==1) %>% 
  filter(particip_nr==0) 
```

## z-standardize

prereg: "... and both attachment anxiety and avoidance as predictors, which will be z-standardized."

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

# Z-standardize attachment variables (for RQ1 logistic analyses)
df_atta_rq1 <- df_atta_rq1 %>%
  mutate(across(
    c(avoide, avoida, avoidb, avoidc, avoidd,
      anxietye, anxietya, anxietyb, anxietyc, anxietyd),
    ~ as.numeric(scale(.)),
    .names = "{.col}_z"))
```

## Keep relevant variables

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

df_atta_rq1 <- df_atta_rq1 %>%
  select(pid, 
         single_consist, single_later_partn, 
         age_base, man, woman,
         ends_with("_z"),
         education, religion, politics, libcon, involved)

df_atta_rq1 <- df_atta_rq1 %>% 
  mutate(grp = case_when(single_consist==1 ~ "Consistently single people",
                         single_later_partn==1 ~ "Initially single, later partnered",
                         .default = NA_character_)) %>% 
  mutate(group_fct_rq1 = factor(grp, 
                            levels = c("Consistently single people", "Initially single, later partnered"), 
                            labels = c("Consistently single people", "Initially single, later partnered"), ordered = TRUE)) %>%
  select(-grp)

table(df_atta_rq1$group_fct_rq1) # looks good
```

# Longitudinal: Keep relevant variables

```{r}
#| echo: true
#| warning: false
#| output: true

df_atta <- df_atta %>% 
  select(pid, particip_nr, starts_with("time_"),
         single_consist, partner_consist, partner_interm, 
         age_base, man, woman, 
         starts_with(c("avoid", "anxiet")), swb,
         education, religion, politics, libcon, involved,
         starts_with("event_"))
```

# Save cleaned data

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false

base::save(df_atta, file = "data/cleaned/df_atta.rda")
base::save(df_atta_rq1, file = "data/cleaned/df_atta_rq1.rda")
```

# Packages used

```{r pkgs}
pkgs <- grateful::cite_packages(output = "table", out.dir = ".")
knitr::kable(pkgs)
```
