---
title: "Change In Single People’s Attachment And Co-Development With Life Satisfaction"
author: "[blinded]" 
toc: true
toc-depth: 6
toc-title: Contents
number-sections: true
execute:
  cache: true
format:
#  docx:
#    highlight-style: github
  html:
    link-external-icon: true
    link-external-newwindow: true
    code-block-bg: true
    code-block-border-left: "#31BAE9"
    embed-resources: true
    theme: default
#comments:
#  hypothesis: true
editor: source
bibliography: 
#  - document_citations.bib
  - grateful-refs.bib
csl: apa.csl
---

Preregistration link: https://osf.io/2udxh/overview?view_only=ee21adb66c6e48a39b3bc53e9fae919b

# Preparations 

## Load packages

```{r}
#| echo: true
#| warning: false
#| cache: false

library(tidyverse)
library(lavaan)
library(grateful)
library(knitr)
library(cowplot)
library(Hmisc)
library(corrplot)
library(purrr)
library(broom)
library(kableExtra)
library(ggh4x)
```

Globals:
```{r}
#| echo: true
#| warning: false
#| cache: false

avoi_short <- c("avoi_glo", "avoi_rom", "avoi_fri", "avoi_mot", "avoi_fat")
anxi_short <- c("anxi_glo", "anxi_rom", "anxi_fri", "anxi_mot", "anxi_fat")
outcomes_short <- c(avoi_short, anxi_short)

avoi_maj <- c("Avoidance: Global", "Avoidance: Romantic", "Avoidance: Best Friend", 
              "Avoidance: Mother", "Avoidance: Father")
anxi_maj <- c("Anxiety: Global", "Anxiety: Romantic", "Anxiety: Best Friend", 
              "Anxiety: Mother", "Anxiety: Father")
outcomes_maj <- c(avoi_maj, anxi_maj)

avoi_min <- c("avoidance (global)", "avoidance (romantic)", "avoidance (best friend)", 
              "avoidance (mother)", "avoidance (father)")
anxi_min <- c("anxiety (global)", "anxiety (romantic)", "anxiety (best friend)", 
              "anxiety (mother)", "anxiety (father)")
outcomes_min <- c(avoi_min, anxi_min)

outcomes <- tibble(short = outcomes_short,
                   maj = outcomes_maj,
                   min = outcomes_min)
```

# Load cleaned data

Cleaned, long file containing all waves of survey data from the CHILL study

```{r load}
#| echo: true
#| warning: false
#| output: false
#| cache: false

base::load("data/cleaned/df_atta.rda")
base::load("data/cleaned/df_atta_rq1.rda")
```

## Last data preparation steps

Rename variables (attachment)
```{r}
#| echo: true
#| warning: false
#| output: false
#| cache: false

df_atta <- df_atta %>% 
  rename(avoi_glo = avoide, avoi_rom = avoidc, avoi_fri = avoidd, avoi_mot = avoida, avoi_fat = avoidb,
         anxi_glo = anxietye, anxi_rom = anxietyc, anxi_fri = anxietyd, anxi_mot = anxietya, anxi_fat = anxietyb)

# in RQ1 df:
df_atta_rq1 <- df_atta_rq1 %>% 
  rename(avoi_glo_z = avoide_z, avoi_rom_z = avoidc_z, avoi_fri_z = avoidd_z, avoi_mot_z = avoida_z, avoi_fat_z = avoidb_z,
         anxi_glo_z = anxietye_z, anxi_rom_z = anxietyc_z, anxi_fri_z = anxietyd_z, anxi_mot_z = anxietya_z, anxi_fat_z = anxietyb_z)
```

Forgot to z-standardize age:
```{r}
#| echo: true
#| warning: false
#| output: false
#| cache: false

# here, I'm using each person's first obs for calculating M/SD
age_m <- df_atta %>% group_by(pid) %>% slice_head(n=1) %>% ungroup() %>% 
  summarise(age_m = mean(age_base, na.rm=T)) %>% pull(age_m)
age_sd <- df_atta %>% group_by(pid) %>% slice_head(n=1) %>% ungroup() %>% 
  summarise(age_sd = sd(age_base, na.rm=T)) %>% pull(age_sd)

df_atta <- df_atta %>% 
  mutate(age_base_z = ifelse(!is.na(age_base), (age_base - age_m) / age_sd, NA_real_))
```

Create wide format data for lavaan: 
```{r}
#| echo: true
#| warning: false
#| output: false
#| cache: false

table(df_atta$time_month_rd)

df_atta_wide <- df_atta %>% 
  arrange(pid, time_month_rd) %>% 
  mutate(time_month_rd = sprintf("%02d", time_month_rd)) %>% # add zero padding
  select(-c(2:4, 23:32)) %>% 
  pivot_wider(names_from = time_month_rd,
              names_sep = "_t",
              values_from = c(9:19))
# colnames(df_atta_wide)


# create factor designating the groups
df_atta_wide <- df_atta_wide %>% 
  mutate(grp = case_when(single_consist==1 ~ "Consistently single people",
                         partner_consist==1 ~ "Consistently partnered people",
                         partner_interm==1 ~ "Intermittently partnered people",
                         .default = NA_character_)) %>% 
  mutate(group_fct = factor(grp, 
                            levels = c("Consistently single people", "Consistently partnered people", 
                                       "Intermittently partnered people"), 
                            labels = c("Consistently single people", "Consistently partnered people", 
                                       "Intermittently partnered people"), ordered = TRUE)) %>%
  select(-grp)

table(df_atta_wide$group_fct) # looks good

# ... also add this to long df:
df_atta <- df_atta %>% 
  mutate(grp = case_when(single_consist==1 ~ "Consistently single people",
                         partner_consist==1 ~ "Consistently partnered people",
                         partner_interm==1 ~ "Intermittently partnered people",
                         .default = NA_character_)) %>% 
  mutate(group_fct = factor(grp, 
                            levels = c("Consistently single people", "Consistently partnered people", 
                                       "Intermittently partnered people"), 
                            labels = c("Consistently single people", "Consistently partnered people", 
                                       "Intermittently partnered people"), ordered = TRUE)) %>%
  select(-grp)
```

Build group-specific data frames
```{r}
#| echo: true
#| warning: false
#| output: false
#| cache: false

df_atta_wide_single_c <- df_atta_wide %>% 
  filter(single_consist==1) %>% 
  select(-c(single_consist, partner_consist, partner_interm))

df_atta_wide_partn_c <- df_atta_wide %>% 
  filter(partner_consist==1) %>% 
  select(-c(single_consist, partner_consist, partner_interm))

df_atta_wide_partn_i <- df_atta_wide %>% 
  filter(partner_interm==1) %>% 
  select(-c(single_consist, partner_consist, partner_interm))

# comparison of each partnered group with single
df_atta_wide_single_partn_c <- bind_rows(df_atta_wide_single_c, df_atta_wide_partn_c)
df_atta_wide_single_partn_i <- bind_rows(df_atta_wide_single_c, df_atta_wide_partn_i)
```

# Sample descriptives

## Selection effects sample

### Basic demographics

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true

# sample descriptives
df_atta_rq1 %>% 
  summarise(n = n(), N = n_distinct(pid), fem = round(mean(woman, na.rm=T)*100,2), 
            m_age = round(mean(age_base, na.rm=T), 2), sd_age = round(sd(age_base, na.rm=T), 2)) %>% kable(digits = 2)

# by group:
df_atta_rq1 %>% 
  group_by(group_fct_rq1) %>% 
  summarise(n = n(), N = n_distinct(pid), fem = round(mean(woman, na.rm=T)*100,2), 
            m_age = round(mean(age_base, na.rm=T), 2), sd_age = round(sd(age_base, na.rm=T), 2)) %>% kable(digits = 2)
```

### Socio-demographic indicators

#### Education
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-summary: "Show the code"
#| code-fold: true

education_table <- df_atta_rq1 %>%
  filter(!is.na(education)) %>%
  count(education, name = "n") %>%
  mutate(
    education = factor(
      education,
      levels = 1:9,
      labels = c(
        "[1] Some High School",
        "[2] Currently in High School",
        "[3] Completed High School",
        "[4] Some College/University",
        "[5] Currently in College/University",
        "[6] Completed College/University",
        "[7] Some Graduate/Professional School",
        "[8] Currently in Graduate/Professional School",
        "[9] Completed Graduate/Professional Degree")),
    percent = round(100 * n / sum(n), 2))

education_table %>% kable(digits = 2)

education_table_by_group <- df_atta_rq1 %>%
  mutate(
    education = factor(
      education,
      levels = 1:9,
      labels = c(
        "[1] Some High School",
        "[2] Currently in High School",
        "[3] Completed High School",
        "[4] Some College/University",
        "[5] Currently in College/University",
        "[6] Completed College/University",
        "[7] Some Graduate/Professional School",
        "[8] Currently in Graduate/Professional School",
        "[9] Completed Graduate/Professional Degree"))) %>%
  filter(!is.na(education)) %>%
  count(group_fct_rq1, education, name = "n") %>%
  group_by(group_fct_rq1) %>%
  mutate(percent = round(100 * n / sum(n), 2)) %>%
  ungroup()

education_table_by_group %>% kable(digits = 2)
```

#### Religion 

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-summary: "Show the code"
#| code-fold: true

religion_table <- df_atta_rq1 %>%
  filter(!is.na(religion)) %>%
  count(religion, name = "n") %>%
  mutate(percent = round(100 * n / sum(n), 2))

religion_table %>% kable(digits = 2)

religion_table_by_group <- df_atta_rq1 %>%
  filter(!is.na(religion)) %>%
  count(group_fct_rq1, religion, name = "n") %>%
  group_by(group_fct_rq1) %>%
  mutate(percent = round(100 * n / sum(n), 2)) %>%
  ungroup()

religion_table_by_group %>% kable(digits = 2)
```

#### Politics 

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-summary: "Show the code"
#| code-fold: true

politics_table <- df_atta_rq1 %>%
  mutate(politics = factor(ifelse(is.na(politics), "NA", politics),
                           levels = c("Libertarian", "Very Conservative", "Conservative",
                                      "Slightly Conservative", "Moderate/middle-of-the-road",
                                      "Slightly Liberal", "Liberal", "Very Liberal",
                                      "Other", "noneselected", "NA"))) %>%
  count(politics, name = "n") %>%
  mutate(percent = round(100 * n / sum(n), 2))

politics_table %>% kable(digits = 2)

politics_table_by_group <- df_atta_rq1 %>%
  mutate(politics = factor(ifelse(is.na(politics), "NA", politics),
                           levels = c("Libertarian", "Very Conservative", "Conservative",
                                      "Slightly Conservative", "Moderate/middle-of-the-road",
                                      "Slightly Liberal", "Liberal", "Very Liberal",
                                      "Other", "noneselected", "NA"))) %>%
  count(group_fct_rq1, politics, name = "n") %>%
  group_by(group_fct_rq1) %>%
  mutate(percent = round(100 * n / sum(n), 2)) %>%
  ungroup()

politics_table_by_group %>% kable(digits = 2)
```

## Longitudinal sample

### Basic demographics

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true

# sample descriptives - total
df_atta %>% 
  summarise(n = n(), N = n_distinct(pid), fem = round(mean(woman, na.rm=T)*100,2), 
            m_age = round(mean(age_base, na.rm=T), 2), sd_age = round(sd(age_base, na.rm=T), 2)) %>% kable(digits = 2)
# by group:
df_atta %>% 
  group_by(group_fct) %>% 
  summarise(n = n(), N = n_distinct(pid), fem = round(mean(woman, na.rm=T)*100,2), 
            m_age = round(mean(age_base, na.rm=T), 2), sd_age = round(sd(age_base, na.rm=T), 2)) %>% kable(digits = 2)

# sample descriptives - person-level
df_atta %>% 
  group_by(pid) %>% slice_head(n=1) %>% ungroup() %>% 
  summarise(n = n(), N = n_distinct(pid), fem = round(mean(woman, na.rm=T)*100,2), 
            m_age = round(mean(age_base, na.rm=T), 2), sd_age = round(sd(age_base, na.rm=T), 2)) %>% kable(digits = 2)
# by group:
df_atta %>% 
  group_by(pid) %>% slice_head(n=1) %>% ungroup() %>% 
  group_by(group_fct) %>% 
  summarise(n = n(), N = n_distinct(pid), fem = round(mean(woman, na.rm=T)*100,2), 
            m_age = round(mean(age_base, na.rm=T), 2), sd_age = round(sd(age_base, na.rm=T), 2)) %>% kable(digits = 2)
```

### Socio-demographic indicators

I do all of those on the person-level only (using each person's first wave).

#### Education
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-summary: "Show the code"
#| code-fold: true

education_table_long <- df_atta %>%
  group_by(pid) %>% slice_head(n=1) %>% ungroup() %>% 
  filter(!is.na(education)) %>%
  count(education, name = "n") %>%
  mutate(
    education = factor(
      education,
      levels = 1:9,
      labels = c(
        "[1] Some High School",
        "[2] Currently in High School",
        "[3] Completed High School",
        "[4] Some College/University",
        "[5] Currently in College/University",
        "[6] Completed College/University",
        "[7] Some Graduate/Professional School",
        "[8] Currently in Graduate/Professional School",
        "[9] Completed Graduate/Professional Degree")),
    percent = round(100 * n / sum(n), 2))

education_table_long %>% kable(digits = 2)

education_table_by_group_long <- df_atta %>%
  group_by(pid) %>% slice_head(n=1) %>% ungroup() %>% 
  mutate(
    education = factor(
      education,
      levels = 1:9,
      labels = c(
        "[1] Some High School",
        "[2] Currently in High School",
        "[3] Completed High School",
        "[4] Some College/University",
        "[5] Currently in College/University",
        "[6] Completed College/University",
        "[7] Some Graduate/Professional School",
        "[8] Currently in Graduate/Professional School",
        "[9] Completed Graduate/Professional Degree"))) %>%
  filter(!is.na(education)) %>%
  count(group_fct, education, name = "n") %>%
  group_by(group_fct) %>%
  mutate(percent = round(100 * n / sum(n), 2)) %>%
  ungroup()

education_table_by_group_long %>% kable(digits = 2)
```

#### Religion 

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-summary: "Show the code"
#| code-fold: true

religion_table_long <- df_atta %>%
  group_by(pid) %>% slice_head(n=1) %>% ungroup() %>% 
  filter(!is.na(religion)) %>%
  count(religion, name = "n") %>%
  mutate(percent = round(100 * n / sum(n), 2))

religion_table_long %>% kable(digits = 2)

religion_table_by_group_long <- df_atta %>%
  group_by(pid) %>% slice_head(n=1) %>% ungroup() %>% 
  filter(!is.na(religion)) %>%
  count(group_fct, religion, name = "n") %>%
  group_by(group_fct) %>%
  mutate(percent = round(100 * n / sum(n), 2)) %>%
  ungroup()

religion_table_by_group_long %>% kable(digits = 2)
```

#### Politics 

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-summary: "Show the code"
#| code-fold: true

politics_table_long <- df_atta %>%
  group_by(pid) %>% slice_head(n=1) %>% ungroup() %>% 
  mutate(politics = factor(ifelse(is.na(politics), "NA", politics),
                           levels = c("Libertarian", "Very Conservative", "Conservative",
                                      "Slightly Conservative", "Moderate/middle-of-the-road",
                                      "Slightly Liberal", "Liberal", "Very Liberal",
                                      "Other", "noneselected", "NA"))) %>%
  count(politics, name = "n") %>%
  mutate(percent = round(100 * n / sum(n), 2))

politics_table_long %>% kable(digits = 2)

politics_table_by_group_long <- df_atta %>%
  group_by(pid) %>% slice_head(n=1) %>% ungroup() %>% 
  mutate(politics = factor(ifelse(is.na(politics), "NA", politics),
                           levels = c("Libertarian", "Very Conservative", "Conservative",
                                      "Slightly Conservative", "Moderate/middle-of-the-road",
                                      "Slightly Liberal", "Liberal", "Very Liberal",
                                      "Other", "noneselected", "NA"))) %>%
  count(group_fct, politics, name = "n") %>%
  group_by(group_fct) %>%
  mutate(percent = round(100 * n / sum(n), 2)) %>%
  ungroup()

politics_table_by_group_long %>% kable(digits = 2)
```

### Correlation matrices

Compute correlation matrices across time: I'm just using the first 3 months here as examples.  

```{r}
#| echo: true
#| warning: false
#| output: true
#| code-fold: true
#| code-summary: "Show the code"
#| cache: true

vars_m1 <- df_atta %>% 
  filter(time_month_rd==1) %>% 
  select(all_of(avoi_short), all_of(anxi_short), swb, single_consist, partner_consist, partner_interm)
cormat_m1 <- Hmisc::rcorr(as.matrix(vars_m1), type="pearson") # uses pairwise complete pairs
cormat_m1 <- cormat_m1$r

vars_m2 <- df_atta %>% 
  filter(time_month_rd==2) %>% 
  select(all_of(avoi_short), all_of(anxi_short), swb, single_consist, partner_consist, partner_interm)
cormat_m2 <- Hmisc::rcorr(as.matrix(vars_m2), type="pearson") # uses pairwise complete pairs
cormat_m2 <- cormat_m2$r

vars_m3 <- df_atta %>% 
  filter(time_month_rd==3) %>% 
  select(all_of(avoi_short), all_of(anxi_short), swb, single_consist, partner_consist, partner_interm)
cormat_m3 <- Hmisc::rcorr(as.matrix(vars_m3), type="pearson") # uses pairwise complete pairs
cormat_m3 <- cormat_m3$r

names_mat <- c(outcomes$maj, "Life Satisfaction", "Consistently single", "Consistently partnered", 
                                       "Intermittently partnered")

rownames(cormat_m1) <- names_mat
colnames(cormat_m1) <- names_mat
rownames(cormat_m2) <- names_mat
colnames(cormat_m2) <- names_mat
rownames(cormat_m3) <- names_mat
colnames(cormat_m3) <- names_mat
```

Plot: Correlation matrix at month 1
```{r}
#| echo: true
#| fig-width: 9
#| fig-height: 7
#| code-fold: true
#| code-summary: "Show the code"
#| cache: true
col <- colorRampPalette(c("#BB4444", "#EE9988", "#FFFFFF", "#77AADD", "#4477AA"))

corrplot(cormat_m1, method="color", col=col(200),  
         type="lower", order="original", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=15, #Text label color and rotation
         diag=T)
```

Plot: Correlation matrix at month 2
```{r}
#| echo: true
#| fig-width: 9
#| fig-height: 7
#| code-fold: true
#| code-summary: "Show the code"
#| cache: true

corrplot(cormat_m2, method="color", col=col(200),  
         type="lower", order="original", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=15, #Text label color and rotation
         diag=T)
```

Plot: Correlation matrix at month 3
```{r}
#| echo: true
#| fig-width: 9
#| fig-height: 7
#| code-fold: true
#| code-summary: "Show the code"
#| cache: true

corrplot(cormat_m3, method="color", col=col(200),  
         type="lower", order="original", 
         addCoef.col = "black", # Add coefficient of correlation
         tl.col="black", tl.srt=15, #Text label color and rotation
         diag=T)
```

::: {.callout-note appearance="minimal"}
Structure of associations is quite similar over time!    
:::

### Variable distributions

#### Avoidance

Prepare df:
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

df_distr_plot_avoi <- df_atta %>% 
  filter(time_month_rd %in% c(1:5)) %>% 
  rename(wave = time_month_rd) %>% 
  select(wave, all_of(avoi_short), swb) %>% 
  pivot_longer(cols = c(avoi_short, "swb"),
    names_to = "variable",
    values_to = "value") %>% 
  mutate(
    variable = factor(variable, levels = c(avoi_short, "swb"), labels = c(avoi_maj, "Life Satisfaction")), # relabel
    wave = factor(wave, levels = c(1:5), labels = c("M1", "M2", "M3", "M4", "M5"))
  )
```

Plot distributions across time: 
```{r}
#| echo: true
#| fig-width: 7
#| fig-height: 9
#| code-fold: true
#| code-summary: "Show the code"
#| cache: true
#| warning: false

ggplot(df_distr_plot_avoi %>% filter(!is.na(value)), aes(x = wave, y = value, fill = wave, color = wave)) +
  geom_boxplot(fill = NA) + 
  geom_violin(fill = NA) + 
  # Add the mean
  stat_summary(
    fun = mean,                 # calculate mean
    geom = "point",             # draw as points
    shape = 23,                 # filled diamond
    size = 3,                   # point size
    color = "black",            # border color
    fill = "yellow"             # fill color of the diamond
  ) +
  facet_wrap(~variable, scales = "free_y", ncol=2) +
  labs(x = "Month", y = "Score", title = "Distributions") +
  theme_bw() +
  theme(legend.position = "none")
```

Yellow diamonds represent the sample means. Bars of boxplot represent the median.  

#### Anxiety

Prepare df:
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

df_distr_plot_anxi <- df_atta %>% 
  filter(time_month_rd %in% c(1:5)) %>% 
  rename(wave = time_month_rd) %>% 
  select(wave, all_of(anxi_short), swb) %>% 
  pivot_longer(cols = c(anxi_short, "swb"),
    names_to = "variable",
    values_to = "value") %>% 
  mutate(
    variable = factor(variable, levels = c(anxi_short, "swb"), labels = c(anxi_maj, "Life Satisfaction")), # relabel
    wave = factor(wave, levels = c(1:5), labels = c("M1", "M2", "M3", "M4", "M5"))
  )
```

Plot distributions across time: 
```{r}
#| echo: true
#| fig-width: 7
#| fig-height: 9
#| code-fold: true
#| code-summary: "Show the code"
#| cache: true
#| warning: false

ggplot(df_distr_plot_anxi %>% filter(!is.na(value)), aes(x = wave, y = value, fill = wave, color = wave)) +
  geom_boxplot(fill = NA) + 
  geom_violin(fill = NA) + 
  # Add the mean
  stat_summary(
    fun = mean,                 # calculate mean
    geom = "point",             # draw as points
    shape = 23,                 # filled diamond
    size = 3,                   # point size
    color = "black",            # border color
    fill = "yellow"             # fill color of the diamond
  ) +
  facet_wrap(~variable, scales = "free_y", ncol=2) +
  labs(x = "Month", y = "Score", title = "Distributions") +
  theme_bw() +
  theme(legend.position = "none")
```

Yellow diamonds represent the sample means. Bars of boxplot represent the median.  

### Descriptives over time

Show means/SD over time: avoidance vars
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

df_atta %>%
  rename(month = time_month_rd) %>% 
  group_by(month) %>%
  summarise(
    n = n(),
    `Avoid.: Global`      = sprintf("%.2f (%.2f)", mean(avoi_glo, na.rm = TRUE), sd(avoi_glo, na.rm = TRUE)),
    `Avoid.: Romantic`    = sprintf("%.2f (%.2f)", mean(avoi_rom, na.rm = TRUE), sd(avoi_rom, na.rm = TRUE)),
    `Avoid.: Best Friend` = sprintf("%.2f (%.2f)", mean(avoi_fri, na.rm = TRUE), sd(avoi_fri, na.rm = TRUE)),
    `Avoid.: Mother`      = sprintf("%.2f (%.2f)", mean(avoi_mot, na.rm = TRUE), sd(avoi_mot, na.rm = TRUE)),
    `Avoid.: Father`      = sprintf("%.2f (%.2f)", mean(avoi_fat, na.rm = TRUE), sd(avoi_fat, na.rm = TRUE)),
    `LS`      = sprintf("%.2f (%.2f)", mean(swb, na.rm = TRUE), sd(swb, na.rm = TRUE))
  ) %>%
  kable()
```

Show means/SD over time: anxiety vars
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

df_atta %>%
  rename(month = time_month_rd) %>% 
  group_by(month) %>%
  summarise(
    n = n(),
    `Anx.: Global`      = sprintf("%.2f (%.2f)", mean(anxi_glo, na.rm = TRUE), sd(anxi_glo, na.rm = TRUE)),
    `Anx.: Romantic`    = sprintf("%.2f (%.2f)", mean(anxi_rom, na.rm = TRUE), sd(anxi_rom, na.rm = TRUE)),
    `Anx.: Best Friend` = sprintf("%.2f (%.2f)", mean(anxi_fri, na.rm = TRUE), sd(anxi_fri, na.rm = TRUE)),
    `Anx.: Mother`      = sprintf("%.2f (%.2f)", mean(anxi_mot, na.rm = TRUE), sd(anxi_mot, na.rm = TRUE)),
    `Anx.: Father`      = sprintf("%.2f (%.2f)", mean(anxi_fat, na.rm = TRUE), sd(anxi_fat, na.rm = TRUE)),
    `LS`      = sprintf("%.2f (%.2f)", mean(swb, na.rm = TRUE), sd(swb, na.rm = TRUE))
  ) %>%
  kable()
```

#### For each group

##### Consistently single people

Show means/SD over time: avoidance vars
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

df_atta %>%
  filter(group_fct=="Consistently single people") %>% 
  rename(month = time_month_rd) %>% 
  group_by(month) %>%
  summarise(
    n = n(),
    `Avoid.: Global`      = sprintf("%.2f (%.2f)", mean(avoi_glo, na.rm = TRUE), sd(avoi_glo, na.rm = TRUE)),
    `Avoid.: Romantic`    = sprintf("%.2f (%.2f)", mean(avoi_rom, na.rm = TRUE), sd(avoi_rom, na.rm = TRUE)),
    `Avoid.: Best Friend` = sprintf("%.2f (%.2f)", mean(avoi_fri, na.rm = TRUE), sd(avoi_fri, na.rm = TRUE)),
    `Avoid.: Mother`      = sprintf("%.2f (%.2f)", mean(avoi_mot, na.rm = TRUE), sd(avoi_mot, na.rm = TRUE)),
    `Avoid.: Father`      = sprintf("%.2f (%.2f)", mean(avoi_fat, na.rm = TRUE), sd(avoi_fat, na.rm = TRUE)),
    `LS`      = sprintf("%.2f (%.2f)", mean(swb, na.rm = TRUE), sd(swb, na.rm = TRUE))
  ) %>%
  kable()
```

Show means/SD over time: anxiety vars
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

df_atta %>%
  filter(group_fct=="Consistently single people") %>% 
  rename(month = time_month_rd) %>% 
  group_by(month) %>%
  summarise(
    n = n(),
    `Anx.: Global`      = sprintf("%.2f (%.2f)", mean(anxi_glo, na.rm = TRUE), sd(anxi_glo, na.rm = TRUE)),
    `Anx.: Romantic`    = sprintf("%.2f (%.2f)", mean(anxi_rom, na.rm = TRUE), sd(anxi_rom, na.rm = TRUE)),
    `Anx.: Best Friend` = sprintf("%.2f (%.2f)", mean(anxi_fri, na.rm = TRUE), sd(anxi_fri, na.rm = TRUE)),
    `Anx.: Mother`      = sprintf("%.2f (%.2f)", mean(anxi_mot, na.rm = TRUE), sd(anxi_mot, na.rm = TRUE)),
    `Anx.: Father`      = sprintf("%.2f (%.2f)", mean(anxi_fat, na.rm = TRUE), sd(anxi_fat, na.rm = TRUE)),
    `LS`      = sprintf("%.2f (%.2f)", mean(swb, na.rm = TRUE), sd(swb, na.rm = TRUE))
  ) %>%
  kable()
```

##### Consistently partnered people

Show means/SD over time: avoidance vars
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

df_atta %>%
  filter(group_fct=="Consistently partnered people") %>% 
  rename(month = time_month_rd) %>% 
  group_by(month) %>%
  summarise(
    n = n(),
    `Avoid.: Global`      = sprintf("%.2f (%.2f)", mean(avoi_glo, na.rm = TRUE), sd(avoi_glo, na.rm = TRUE)),
    `Avoid.: Romantic`    = sprintf("%.2f (%.2f)", mean(avoi_rom, na.rm = TRUE), sd(avoi_rom, na.rm = TRUE)),
    `Avoid.: Best Friend` = sprintf("%.2f (%.2f)", mean(avoi_fri, na.rm = TRUE), sd(avoi_fri, na.rm = TRUE)),
    `Avoid.: Mother`      = sprintf("%.2f (%.2f)", mean(avoi_mot, na.rm = TRUE), sd(avoi_mot, na.rm = TRUE)),
    `Avoid.: Father`      = sprintf("%.2f (%.2f)", mean(avoi_fat, na.rm = TRUE), sd(avoi_fat, na.rm = TRUE)),
    `LS`      = sprintf("%.2f (%.2f)", mean(swb, na.rm = TRUE), sd(swb, na.rm = TRUE))
  ) %>%
  kable()
```

Show means/SD over time: anxiety vars
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

df_atta %>%
  filter(group_fct=="Consistently partnered people") %>% 
  rename(month = time_month_rd) %>% 
  group_by(month) %>%
  summarise(
    n = n(),
    `Anx.: Global`      = sprintf("%.2f (%.2f)", mean(anxi_glo, na.rm = TRUE), sd(anxi_glo, na.rm = TRUE)),
    `Anx.: Romantic`    = sprintf("%.2f (%.2f)", mean(anxi_rom, na.rm = TRUE), sd(anxi_rom, na.rm = TRUE)),
    `Anx.: Best Friend` = sprintf("%.2f (%.2f)", mean(anxi_fri, na.rm = TRUE), sd(anxi_fri, na.rm = TRUE)),
    `Anx.: Mother`      = sprintf("%.2f (%.2f)", mean(anxi_mot, na.rm = TRUE), sd(anxi_mot, na.rm = TRUE)),
    `Anx.: Father`      = sprintf("%.2f (%.2f)", mean(anxi_fat, na.rm = TRUE), sd(anxi_fat, na.rm = TRUE)),
    `LS`      = sprintf("%.2f (%.2f)", mean(swb, na.rm = TRUE), sd(swb, na.rm = TRUE))
  ) %>%
  kable()
```

##### Intermittently partnered people

Show means/SD over time: avoidance vars
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

df_atta %>%
  filter(group_fct=="Intermittently partnered people") %>% 
  rename(month = time_month_rd) %>% 
  group_by(month) %>%
  summarise(
    n = n(),
    `Avoid.: Global`      = sprintf("%.2f (%.2f)", mean(avoi_glo, na.rm = TRUE), sd(avoi_glo, na.rm = TRUE)),
    `Avoid.: Romantic`    = sprintf("%.2f (%.2f)", mean(avoi_rom, na.rm = TRUE), sd(avoi_rom, na.rm = TRUE)),
    `Avoid.: Best Friend` = sprintf("%.2f (%.2f)", mean(avoi_fri, na.rm = TRUE), sd(avoi_fri, na.rm = TRUE)),
    `Avoid.: Mother`      = sprintf("%.2f (%.2f)", mean(avoi_mot, na.rm = TRUE), sd(avoi_mot, na.rm = TRUE)),
    `Avoid.: Father`      = sprintf("%.2f (%.2f)", mean(avoi_fat, na.rm = TRUE), sd(avoi_fat, na.rm = TRUE)),
    `LS`      = sprintf("%.2f (%.2f)", mean(swb, na.rm = TRUE), sd(swb, na.rm = TRUE))
  ) %>%
  kable()
```

Show means/SD over time: anxiety vars
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

df_atta %>%
  filter(group_fct=="Intermittently partnered people") %>% 
  rename(month = time_month_rd) %>% 
  group_by(month) %>%
  summarise(
    n = n(),
    `Anx.: Global`      = sprintf("%.2f (%.2f)", mean(anxi_glo, na.rm = TRUE), sd(anxi_glo, na.rm = TRUE)),
    `Anx.: Romantic`    = sprintf("%.2f (%.2f)", mean(anxi_rom, na.rm = TRUE), sd(anxi_rom, na.rm = TRUE)),
    `Anx.: Best Friend` = sprintf("%.2f (%.2f)", mean(anxi_fri, na.rm = TRUE), sd(anxi_fri, na.rm = TRUE)),
    `Anx.: Mother`      = sprintf("%.2f (%.2f)", mean(anxi_mot, na.rm = TRUE), sd(anxi_mot, na.rm = TRUE)),
    `Anx.: Father`      = sprintf("%.2f (%.2f)", mean(anxi_fat, na.rm = TRUE), sd(anxi_fat, na.rm = TRUE)),
    `LS`      = sprintf("%.2f (%.2f)", mean(swb, na.rm = TRUE), sd(swb, na.rm = TRUE))
  ) %>%
  kable()
```

### Plots: linear trends

Only focusing on the first 30 months for now to make this easier to read!  

Create df:  
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false
#| code-fold: true
#| code-summary: "Show the code"

attach_long <- df_atta %>%
  filter(time_month_rd <= 29) %>%
  select(pid, time_month_rd, all_of(avoi_short), all_of(anxi_short), group_fct) %>%
  pivot_longer(
    cols = -c(pid, time_month_rd, group_fct),
    names_to = c("type", "construct"),
    names_pattern = "(avoi|anxi)_(.*)",
    values_to = "value") %>%
  mutate(
    construct = recode(construct,
                       glo = "Global",
                       rom = "Romantic",
                       fri = "Best Friend",
                       mot = "Mother",
                       fat = "Father"),
    construct = factor(construct,
                       levels = c("Global", "Romantic", "Best Friend", "Mother", "Father")),
    type = recode(type,
                  avoi = "Avoidance",
                  anxi = "Anxiety"))

summary_attach <- attach_long %>%
  group_by(construct, type, time_month_rd) %>%
  summarise(
    mean_val = mean(value, na.rm = TRUE),
    se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
    n = sum(!is.na(value)),
    .groups = "drop") %>%
  mutate(ci_lower = mean_val - 1.96 * se,
         ci_upper = mean_val + 1.96 * se)

# by group:
summary_attach_group <- attach_long %>%
  group_by(construct, type, time_month_rd, group_fct) %>%
  summarise(
    mean_val = mean(value, na.rm = TRUE),
    se = sd(value, na.rm = TRUE) / sqrt(sum(!is.na(value))),
    n = sum(!is.na(value)),
    .groups = "drop") %>%
  mutate(ci_lower = mean_val - 1.96 * se,
         ci_upper = mean_val + 1.96 * se)
```

Show plot:
```{r}
#| echo: true
#| fig-width: 7
#| fig-height: 9
#| code-fold: true
#| code-summary: "Show the code"
#| cache: false
#| warning: false

ggplot(summary_attach,
       aes(x = time_month_rd, y = mean_val, color = type, group = type)) +
  geom_line(size = 1, position = position_dodge(width = 0.2)) +
  geom_point(size = 0.5, position = position_dodge(width = 0.2)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2, position = position_dodge(width = 0.2)) +
  facet_wrap(~ construct, ncol = 1, scales = "free_y") +
  scale_x_continuous(breaks = seq(0, 29, 2)) +
  labs(
    title = "Attachment Avoidance and Anxiety Across the First 30 Months",
    x = "Month",
    y = "Mean Value",
    color = "Attachment Dimension"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))
```

Confidence intervals are difficult to see in this view but they are there...

#### Group comparisons

But now separately for avoidance and anxiety (otherwise too difficult to see)  

Show plot - avoidance:  
```{r}
#| echo: true
#| fig-width: 7
#| fig-height: 9
#| code-fold: true
#| code-summary: "Show the code"
#| cache: false
#| warning: false

ggplot(summary_attach_group %>% filter(type=="Avoidance"),
       aes(x = time_month_rd, y = mean_val, color = group_fct, group = group_fct)) +
  geom_line(size = 0.75, position = position_dodge(width = 0.2)) +
  geom_point(size = 1.1, position = position_dodge(width = 0.2)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2, position = position_dodge(width = 0.2)) +
  facet_wrap(~ construct, ncol = 1, scales = "free_y") +
  scale_x_continuous(breaks = seq(0, 29, 2)) +
  scale_color_manual(values = c("#0072B2", "#D55E00", "#009E73", "#CC79A7", "#56B4E9", "#E69F00")) +
  labs(
    title = "Attachment Avoidance Across the First 30 Months",
    x = "Month",
    y = "Mean Value",
    color = "Group"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))
```

Show plot - anxiety:  
```{r}
#| echo: true
#| fig-width: 7
#| fig-height: 9
#| code-fold: true
#| code-summary: "Show the code"
#| cache: false
#| warning: false

ggplot(summary_attach_group %>% filter(type=="Anxiety"),
       aes(x = time_month_rd, y = mean_val, color = group_fct, group = group_fct)) +
  geom_line(size = 0.75, position = position_dodge(width = 0.2)) +
  geom_point(size = 1.1, position = position_dodge(width = 0.2)) +
  geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0.2, position = position_dodge(width = 0.2)) +
  facet_wrap(~ construct, ncol = 1, scales = "free_y") +
  scale_x_continuous(breaks = seq(0, 29, 2)) +
  scale_color_manual(values = c("#0072B2", "#D55E00", "#009E73", "#CC79A7", "#56B4E9", "#E69F00")) +
  labs(
    title = "Attachment Anxiety Across the First 30 Months",
    x = "Month",
    y = "Mean Value",
    color = "Group"
  ) +
  theme_minimal(base_size = 14) +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(ncol = 2))
```

### Attrition analyses

#### Baseline predictors of study progress/completion

Reaching 12 / 24 months in the survey  

Create df:
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true

df_completion <- df_atta %>%
  group_by(pid) %>%
  summarise(last_month = max(time_month_rd, na.rm = TRUE),
            completed_12m = as.integer(last_month >= 12),
            completed_24m = as.integer(last_month >= 24))

table(df_completion$completed_12m)
prop.table(table(df_completion$completed_12m))

table(df_completion$completed_24m)
prop.table(table(df_completion$completed_24m))

# Merge with baseline variables
df_baseline <- df_atta %>%
  filter(time_month_rd == 0) %>%
  left_join(df_completion, by = "pid")
```

Run models (12 months):
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

preds <- c(
  "single_consist", "partner_consist", 
  "age_base", "man", 
  "avoi_glo", "avoi_mot", "avoi_fat", "avoi_rom", "avoi_fri",
  "anxi_glo", "anxi_mot", "anxi_fat", "anxi_rom", "anxi_fri",
  "swb"
)

# Fit all univariate models
uni_results_12 <- map_dfr(preds, function(x){

  fit <- glm(
    reformulate(x, response = "completed_12m"),
    family = binomial,
    data = df_baseline)

  tidy(fit, conf.int = TRUE, exponentiate = TRUE) %>%
    filter(term != "(Intercept)") %>%
    mutate(predictor = x)
})

# Fit the joint model
joint_fit_12 <- glm(
  reformulate(preds, response = "completed_12m"),
  family = binomial,
  data = df_baseline)

joint_results_12 <-
  tidy(joint_fit_12, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term != "(Intercept)")
```

Show results (12 months):
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

results_12 <- uni_results_12 %>%
  select(predictor,
         uni_OR = estimate,
         uni_low = conf.low,
         uni_high = conf.high,
         uni_p = p.value) %>%
  left_join(
    joint_results_12 %>%
      select(term,
             joint_OR = estimate,
             joint_low = conf.low,
             joint_high = conf.high,
             joint_p = p.value),
    by = c("predictor" = "term"))

results_12 <- results_12 %>%
  mutate(
    `Univariate OR (95% CI)` =
      sprintf("%.2f (%.2f, %.2f)", uni_OR, uni_low, uni_high),

    `Joint OR (95% CI)` =
      sprintf("%.2f (%.2f, %.2f)", joint_OR, joint_low, joint_high),

    `Univariate p` = scales::pvalue(uni_p),
    `Joint p` = scales::pvalue(joint_p)) %>%
  select(
    Predictor = predictor,
    `Univariate OR (95% CI)`,
    `Univariate p`,
    `Joint OR (95% CI)`,
    `Joint p`)

knitr::kable(
  results_12,
  align = c("l", "c", "c", "c", "c"),
  caption = "Baseline predictors of completing the 12-month assessment."
)
```

Run models (24 months):
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

# Fit all univariate models
uni_results_24 <- map_dfr(preds, function(x){

  fit <- glm(
    reformulate(x, response = "completed_24m"),
    family = binomial,
    data = df_baseline)

  tidy(fit, conf.int = TRUE, exponentiate = TRUE) %>%
    filter(term != "(Intercept)") %>%
    mutate(predictor = x)
})

# Fit the joint model
joint_fit_24 <- glm(
  reformulate(preds, response = "completed_24m"),
  family = binomial,
  data = df_baseline)

joint_results_24 <-
  tidy(joint_fit_24, conf.int = TRUE, exponentiate = TRUE) %>%
  filter(term != "(Intercept)")
```

Show results (24 months):
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

results_24 <- uni_results_24 %>%
  select(predictor,
         uni_OR = estimate,
         uni_low = conf.low,
         uni_high = conf.high,
         uni_p = p.value) %>%
  left_join(
    joint_results_24 %>%
      select(term,
             joint_OR = estimate,
             joint_low = conf.low,
             joint_high = conf.high,
             joint_p = p.value),
    by = c("predictor" = "term"))

results_24 <- results_24 %>%
  mutate(
    `Univariate OR (95% CI)` =
      sprintf("%.2f (%.2f, %.2f)", uni_OR, uni_low, uni_high),

    `Joint OR (95% CI)` =
      sprintf("%.2f (%.2f, %.2f)", joint_OR, joint_low, joint_high),

    `Univariate p` = scales::pvalue(uni_p),
    `Joint p` = scales::pvalue(joint_p)) %>%
  select(
    Predictor = predictor,
    `Univariate OR (95% CI)`,
    `Univariate p`,
    `Joint OR (95% CI)`,
    `Joint p`)

knitr::kable(
  results_24,
  align = c("l", "c", "c", "c", "c"),
  caption = "Baseline predictors of completing the 24-month assessment."
)
```

::: {.callout-note appearance="minimal"}
Comparison/reference group here are the intermittently partnered people (who have a much higher likelihood of study completion!). Other variables don't seem to matter much.  
:::

#### Number of completed assessments

Create df:
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

# number of completed assessments
df_nassess <- df_atta %>%
  group_by(pid) %>%
  summarise(n_assess = n(),
            .groups = "drop")

# Merge with baseline
df_baseline_compl <- df_atta %>%
  filter(time_month_rd == 0) %>%
  left_join(df_nassess, by = "pid")
```

Run models:
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

# univariate models
uni_results_compl <- map_dfr(preds, \(x){

  fit <- lm(
    reformulate(x, response = "n_assess"),
    data = df_baseline_compl
  )

  tidy(fit, conf.int = TRUE) %>%
    filter(term != "(Intercept)") %>%
    mutate(predictor = x)
})

# Joint model
joint_fit_compl <- lm(
  reformulate(preds, response = "n_assess"),
  data = df_baseline_compl
)

joint_results_compl <- tidy(joint_fit_compl, conf.int = TRUE) %>%
  filter(term != "(Intercept)")
```

Merge and show as table:
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

results_compl <- uni_results_compl %>%
  select(predictor,
         uni_b = estimate,
         uni_low = conf.low,
         uni_high = conf.high,
         uni_p = p.value) %>%
  left_join(
    joint_results_compl %>%
      select(term,
             joint_b = estimate,
             joint_low = conf.low,
             joint_high = conf.high,
             joint_p = p.value),
    by = c("predictor" = "term")
  )

results_compl <- results_compl %>%
  mutate(
    `Univariate b (95% CI)` =
      sprintf("%.2f (%.2f, %.2f)", uni_b, uni_low, uni_high),

    `Joint b (95% CI)` =
      sprintf("%.2f (%.2f, %.2f)", joint_b, joint_low, joint_high),

    `Univariate p` = scales::pvalue(uni_p),
    `Joint p` = scales::pvalue(joint_p)
  ) %>%
  select(
    Predictor = predictor,
    `Univariate b (95% CI)`,
    `Univariate p`,
    `Joint b (95% CI)`,
    `Joint p`
  )

knitr::kable(results_compl)
```

::: {.callout-note appearance="minimal"}
Comparison/reference group here are the intermittently partnered people (who completed more waves!). Similar picture here compared to reaching 12/24 month mark. In addition, younger people seemed to have completed more total waves.   
:::

#### Proportion of missingness over time

Check missingness proportions over time:

(These are very similar across the different outcomes - doesn't really matter which one I look at!)
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false
#| code-fold: true
#| code-summary: "Show the code"

df_attrition <- df_atta_wide %>%
  select(starts_with("avoi_glo_t")) %>%
  pivot_longer(
    cols = everything(),
    names_to = "month",
    names_pattern = "avoi_glo_t(\\d+)",
    values_to = "value"
  ) %>%
  mutate(month = as.integer(month))

missing_summary <- df_attrition %>%
  group_by(month) %>%
  summarise(
    prop_missing = mean(is.na(value)),
    n_available = sum(!is.na(value)),
    n_total = n(),
    .groups = "drop"
  )
```

Show plot:
```{r}
#| echo: true
#| fig-width: 7
#| fig-height: 9
#| code-fold: true
#| code-summary: "Show the code"
#| cache: false
#| warning: false

ggplot(missing_summary, aes(x = month, y = prop_missing)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
  scale_y_continuous(labels = scales::percent) +
  scale_x_continuous(breaks = seq(0, 35, 5)) +
  labs(
    title = "Proportion Missing Across 36 Months\n(Avoidance: Global)",
    x = "Month",
    y = "Proportion Missing"
  ) +
  theme_minimal(base_size = 14)
```

# Confirmatory analyses

## RQ1: Prospective Selection Effects

From prereg: "In the sample of single people at baseline, we will run logistic regression models (with a logit link function) with consistent singlehood (0 = no, initially single but later find partner, 1 = yes, consistently single) as the outcome and both attachment anxiety and avoidance as predictors, which will be z-standardized. We will also include age and gender as control variables. Thus, we will run joint models for anxiety and avoidance but separate models for global attachment and each domain of attachment (i.e., in total 5 models with different attachment domains)."  

Logistic regression = pure between-person comparison  

Global attachment:  

```{r selection-logistic-glo}
#| echo: true
#| cache: true
#| warning: false

formula_sel_glo <- as.formula(
  paste("single_consist", "~", paste(c("avoi_glo_z", "anxi_glo_z", "age_base", "man"), collapse = " + ")))

print(formula_sel_glo)

sel_glo <- glm(formula_sel_glo, 
                   family = binomial(link='logit'), data = df_atta_rq1)
summary(sel_glo)
```

Romantic attachment:  

```{r selection-logistic-rom}
#| echo: true
#| cache: true
#| warning: false

formula_sel_rom <- as.formula(
  paste("single_consist", "~", paste(c("avoi_rom_z", "anxi_rom_z", "age_base", "man"), collapse = " + ")))

print(formula_sel_rom)

sel_rom <- glm(formula_sel_rom, 
                   family = binomial(link='logit'), data = df_atta_rq1)
summary(sel_rom)
```

Friend-specific attachment:  

```{r selection-logistic-fri}
#| echo: true
#| cache: true
#| warning: false

formula_sel_fri <- as.formula(
  paste("single_consist", "~", paste(c("avoi_fri_z", "anxi_fri_z", "age_base", "man"), collapse = " + ")))

print(formula_sel_fri)

sel_fri <- glm(formula_sel_fri, 
                   family = binomial(link='logit'), data = df_atta_rq1)
summary(sel_fri)
```

Mother-specific attachment:  

```{r selection-logistic-mot}
#| echo: true
#| cache: true
#| warning: false

formula_sel_mot <- as.formula(
  paste("single_consist", "~", paste(c("avoi_mot_z", "anxi_mot_z", "age_base", "man"), collapse = " + ")))

print(formula_sel_mot)

sel_mot <- glm(formula_sel_mot, 
                   family = binomial(link='logit'), data = df_atta_rq1)
summary(sel_mot)
```

Father-specific attachment:  

```{r selection-logistic-fat}
#| echo: true
#| cache: true
#| warning: false

formula_sel_fat <- as.formula(
  paste("single_consist", "~", paste(c("avoi_fat_z", "anxi_fat_z", "age_base", "man"), collapse = " + ")))

print(formula_sel_fat)

sel_fat <- glm(formula_sel_fat, 
                   family = binomial(link='logit'), data = df_atta_rq1)
summary(sel_fat)
```

Note: In this case, the predictors are both significant in separate models (avoidance / anxiety). 

### Results table

Gather estimates:
```{r selection-logistic-df}
#| echo: true
#| warning: false
#| output: false
#| code-fold: true
#| code-summary: "Show the code"

df_summa_sel_logist <- bind_rows(
  broom::tidy(sel_glo, conf.int = T, conf.level = .95, exponentiate = TRUE) %>% mutate(domain = "Global"),
  broom::tidy(sel_rom, conf.int = T, conf.level = .95, exponentiate = TRUE) %>% mutate(domain = "Romantic"),
  broom::tidy(sel_fri, conf.int = T, conf.level = .95, exponentiate = TRUE) %>% mutate(domain = "Friend"),
  broom::tidy(sel_mot, conf.int = T, conf.level = .95, exponentiate = TRUE) %>% mutate(domain = "Mother"),
  broom::tidy(sel_fat, conf.int = T, conf.level = .95, exponentiate = TRUE) %>% mutate(domain = "Father"))

df_summa_sel_logist <- df_summa_sel_logist %>% 
  mutate(domain_fct = factor(domain, 
                             levels = c("Global", "Romantic", "Friend", "Mother", "Father"), 
                             labels = c("Global", "Romantic", "Friend", "Mother", "Father"), ordered = TRUE))
```

```{r selection-logistic-table}
#| echo: true
#| warning: false
#| output: true

df_summa_sel_logist %>% 
  filter(term %in% c("avoi_glo_z", "anxi_glo_z",
                     "avoi_rom_z", "anxi_rom_z",
                     "avoi_fri_z", "anxi_fri_z",
                     "avoi_mot_z", "anxi_mot_z",
                     "avoi_fat_z", "anxi_fat_z")) %>%
  mutate(OR = estimate,
    CI_low = conf.low,
    CI_high = conf.high,
    pred = case_when(
      grepl("avoi", term) ~ "Avoidance",
      grepl("anxi", term) ~ "Anxiety"),
    `OR (95% CI)` = sprintf("%.2f (%.2f, %.2f)", OR, CI_low, CI_high),
    p = format.pval(p.value, digits = 3, eps = .001)) %>%
  select(domain, pred, `OR (95% CI)`, p) %>%
  arrange(factor(domain, levels = c("Global", "Romantic", "Friend", "Mother", "Father")),
          pred) %>%
  kable()
```

## RQ2: Changes in Attachment Models

From prereg: "To trace mean-level change in attachment across time, we will run univariate latent growth curve models based on manifest mean scale scores. We will start with separate models in each analysis group (consistently single, consistently partnered, intermittently partnered) and then extend those to multi-group models comparing consistently single people to each of the partnered groups."  

"The linear growth variable will be time at assessment (i.e., months centered at study entry). We run separate models for attachment anxiety and avoidance and for global attachment and each domain (2 x 5 attachment outcomes for each group comparison)."  

I'm doing the main models for all attachment domains in this section even though we only investigate global and romantic as confirmatory and the rest as exploratory. However, the entirely exploratory comparison of consistently single people and intermittently partnered individuals will follow below in the next section.  

### Example model

I'm first creating a template and show this with an example model of global avoidance (in singles, and then extended to single-partnered comparison). Below, I loop through all outcomes using the template.  

#### Single-group models

Specify model template, and show example model output:   

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true

# latent growth curve model: only 1 group
# Define number of assessment waves
n_waves <- 30  # t00 to t29

# Create variable names
times <- sprintf("%02d", 0:(n_waves - 1))
outcome_vars <- paste0("outcome_t", times)

# Intercept loadings
i_loadings <- paste0("1*", outcome_vars, collapse = " + ")

# Slope loadings (scaled 0 to 1)
s_values <- seq(0, 1, length.out = n_waves)
s_loadings <- paste0(round(s_values, 5), "*", outcome_vars, collapse = " + ")

# Residual variance labels
residuals <- paste0(outcome_vars, " ~~ res_", times, "*", outcome_vars, collapse = "\n")

# For plotting: Model-implied trajectory parameters (assuming age_base_z = 0, i.e., sample-average baseline age)
trajectory_estimates <- paste0("pred_t", times, " := a0 + a1*", round(s_values, 5), collapse = "\n")

# LGCM template
rq2_template <- paste0('
# Define intercept and slope factors
i =~ ', i_loadings, '

s =~ ', s_loadings, '

# Regress latent growth factors on baseline age
i ~ bi*age_base_z
s ~ bs*age_base_z

# Mean structure
i ~ a0*1
s ~ a1*1

# Variance structure
i ~~ vi*i
s ~~ vs*s
i ~~ cis*s

# Model-implied trajectories (for plotting)
', trajectory_estimates, '

# Residual variances
', residuals, '
')

# show the template:
cat(rq2_template)

# example model with global avoidance
model_rq2_avoi_glo_example <- stringr::str_replace_all(rq2_template, "outcome", "avoi_glo")

# fit the models - 1 model for single, 1 for partnered
fit_rq2_avoi_glo_example <- lavaan::growth(model_rq2_avoi_glo_example, data = df_atta_wide_single_c, 
                                           missing = "fiml", verbose = FALSE)
summary(fit_rq2_avoi_glo_example, fit.measures = TRUE, standardized = TRUE, ci = FALSE)

fit_rq2_avoi_glo_partn_c_example <- lavaan::growth(model_rq2_avoi_glo_example, data = df_atta_wide_partn_c, 
                                           missing = "fiml", verbose = FALSE)
summary(fit_rq2_avoi_glo_partn_c_example, fit.measures = TRUE, standardized = TRUE, ci = FALSE)
```

::: {.callout-note appearance="minimal"}
Global avoidance decreases over time in both groups, with slightly more pronounced decreases in single people. No significant age moderation (but good that we control for age differences). 
:::


::: {.callout-note appearance="minimal"}
A few warning messages appear:  
- 1 case is dropped because of a missing value in age. No problem, I think. N = 592 now. (as an exogenous variable, missingsness in age is not handled with FIML)  
- Low coverage at later time points: this was to be expected, with increased dropout and up to 30 months of data (e.g., 84% missingness at t20, and 92% at t29). I think it's no big issue here, given that the model still converged, produced no implausible estimates, and resulted in decent fit indices (at least in the traditional ones; some of the "robust" ones could not be estimated properly...)  
- EM estimated variance-covariance matrix (Sigma) is (near) singular: also not surprising given the data structure and missingness -> lavInspect(fit_rq2_avoi_glo_example, "post.check") indicates TRUE, meaning that the final fitted model covariance structure is admissible  
- In pchisq(x2, df = df, ncp = ncp) : NaNs produced -> This may relate to some of the chi-square based fit statistics.  

--> Models were estimated using FIML to account for missing observations. Due to the longitudinal design and increasing attrition at later waves, some covariance estimates were based on limited pairwise coverage. All models converged and yielded admissible solutions.  
--> Below, we provide more details on all models in "Model fit" and "Model diagnostics".  
:::

#### Multi-group model

Extend to multi-group model to compare single (_s) vs. partnered people (_p)  

Freely estimated group differences by default; group-specific age effects; group-specific intercept/slope means; group-specific variances; group-specific residual variances; same time metric across groups (0 -> 1 scaling over 29 months)  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true

# latent growth curve model: multi-group
# ... I dont repeat the parts here that stay the same: n_waves, times, outcome_vars, etc.

# Residual variance labels (group-specific)
residuals_multi <- paste0(outcome_vars, " ~~ c(\"r", times, "_s\", \"r", times, "_p\")*", outcome_vars, collapse = "\n")

# For plotting: Model-implied trajectory parameters (assuming age_base_z = 0, i.e., sample-average baseline age)
trajectory_estimates_multi <- paste0("pred_t", times, "_s := a0_s + a1_s*", round(s_values, 5),
                                     "\n",
                                     "pred_t", times, "_p := a0_p + a1_p*", round(s_values, 5), collapse = "\n")

# Multi-group LGCM template
rq2_template_multi <- paste0('
# Define intercept and slope factors
i =~ ', i_loadings, '

s =~ ', s_loadings, '

# Regress latent growth factors on baseline age
i ~ c("bi_s", "bi_p")*age_base_z
s ~ c("bs_s", "bs_p")*age_base_z

# Mean structure
i ~ c("a0_s", "a0_p")*1
s ~ c("a1_s", "a1_p")*1

# Variance structure
i ~~ c("vi_s", "vi_p")*i
s ~~ c("vs_s", "vs_p")*s
i ~~ c("cis_s", "cis_p")*s

# Model-implied trajectories (for plotting)
', trajectory_estimates_multi, '

# Residual variances
', residuals_multi, '

')

# show the template:
cat(rq2_template_multi)

# Example model with global avoidance
model_rq2_mg_avoi_glo_example <- stringr::str_replace_all(rq2_template_multi, "outcome", "avoi_glo")

# Fit model
fit_rq2_mg_avoi_glo_example <- lavaan::growth(model_rq2_mg_avoi_glo_example,
                                      data = df_atta_wide_single_partn_c %>% arrange(group_fct),
                                      group = "group_fct",
                                      missing = "fiml", verbose = FALSE)

summary(fit_rq2_mg_avoi_glo_example, fit.measures = TRUE, standardized = TRUE, ci = FALSE)
```

::: {.callout-note appearance="minimal"}
Descriptively, the global avoidance decreases are somewhat more pronounced in single people compared to partnered people. Single people start with higher avoidance at baseline, though. The difference in slopes is not sufficient, though, to "offset" this intercept difference. No significant age moderation in either group. 
:::

Formal test of group differences: "Likelihood ratio tests will indicate whether a model constraining the latent slope parameters to be equal across groups fits the data better compared to a model freely estimating them."  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true

# latent growth curve model: multi-group 
# -> create an intermediate model where the latent slope parameter is constrained to be equal across groups

rq2_template_multi_constr <- stringr::str_replace(rq2_template_multi, 
                                                  's ~ c\\("a1_s", "a1_p"\\)\\*1', 's ~ a1*1')
rq2_template_multi_constr <- stringr::str_replace_all(rq2_template_multi_constr, 'a1_s', 'a1')
rq2_template_multi_constr <- stringr::str_replace_all(rq2_template_multi_constr, 'a1_p', 'a1')

model_rq2_mg_avoi_glo_constr <- stringr::str_replace_all(rq2_template_multi_constr, "outcome", "avoi_glo")

fit_rq2_mg_avoi_glo_constr <- lavaan::growth(model_rq2_mg_avoi_glo_constr,
                                                  data = df_atta_wide_single_partn_c %>% arrange(group_fct),
                                                  group = "group_fct",
                                                  missing = "fiml",
                                                  verbose = FALSE)

anova(fit_rq2_mg_avoi_glo_example, fit_rq2_mg_avoi_glo_constr)
```

::: {.callout-note appearance="minimal"}
No significant group differences in the slopes according to LRT.
:::

### Template loop

Run loop over all 5 X 2 outcomes  

(Here, I suppress lavaan warnings in the html output, but they are very similar to the ones shown above for the example model. Below, I go into model diagnostics more systematically.)  

```{r rq2-loop}
#| echo: true
#| warning: false
#| output: false
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

# loop across all attachment outcomes
for (i in 1:length(outcomes$short)) {
#for (i in 1:2) {
  print(paste0("Running outcome: ", outcomes$maj[i]))
  # Step 1: fill single-group model template (2x, 1 for single, 1 for partnered)
  print("-> Step 1")
  model_rq2 <- stringr::str_replace_all(rq2_template, "outcome", outcomes$short[i])
  fit_rq2 <- lavaan::growth(model_rq2,
                            data = df_atta_wide_single_c,
                            missing = "fiml", verbose = FALSE)
  eval(call("<-", as.name(paste0("fit_rq2_", outcomes$short[i])), fit_rq2))
  saveRDS(fit_rq2, file = paste0("models/fit_rq2_", outcomes$short[i], ".rds"))
  
  fit_rq2_partn_c <- lavaan::growth(model_rq2,
                            data = df_atta_wide_partn_c,
                            missing = "fiml", verbose = FALSE)
  eval(call("<-", as.name(paste0("fit_rq2_", outcomes$short[i], "_partn_c")), fit_rq2_partn_c))
  saveRDS(fit_rq2_partn_c, file = paste0("models/fit_rq2_", outcomes$short[i], "_partn_c.rds"))

  # Step 2: fill free multigroup model template
  print("-> Step 2")
  model_rq2_multi <- stringr::str_replace_all(rq2_template_multi, "outcome", outcomes$short[i])
  fit_rq2_multi <- lavaan::growth(model_rq2_multi,
                                  data = df_atta_wide_single_partn_c %>% arrange(group_fct),
                                  group = "group_fct",
                                  missing = "fiml", verbose = FALSE)
  eval(call("<-", as.name(paste0("fit_rq2_mg_", outcomes$short[i])), fit_rq2_multi))
  saveRDS(fit_rq2_multi, file = paste0("models/fit_rq2_mg_", outcomes$short[i], ".rds"))

  # Step 3: fill constrained multigroup model template
  print("-> Step 3")
  model_rq2_multi_constr <- stringr::str_replace_all(rq2_template_multi_constr, "outcome", outcomes$short[i])
  fit_rq2_multi_constr <- lavaan::growth(model_rq2_multi_constr,
                                         data = df_atta_wide_single_partn_c %>% arrange(group_fct),
                                         group = "group_fct",
                                         missing = "fiml", verbose = FALSE)
  eval(call("<-", as.name(paste0("fit_rq2_mg_", outcomes$short[i], "_constr")), fit_rq2_multi_constr))
  saveRDS(fit_rq2_multi_constr, file = paste0("models/fit_rq2_mg_", outcomes$short[i], "_constr.rds"))

  # Step 4: likelihood ratio test: free vs constrained slopes
  print("-> Step 4")
  lrt <- anova(fit_rq2_multi, fit_rq2_multi_constr)
  eval(call("<-", as.name(paste0("lrt_rq2_mg_", outcomes$short[i])), lrt))
}
```

Create summary table of all effects of interest:  

First, parameter extraction  
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

### single-group lavaan models:
# custom function for parameter extraction
extract_lav_rq2 <- function(fit_obj) {
  name_obj <- as.character(substitute(fit_obj))
  name_outc <- name_obj %>% 
    str_remove("fit_rq2_") %>% 
    str_remove("_partn_c$")
  group_lab <- ifelse(str_detect(name_obj, "partn_c$"),
                      "Consistently partnered",
                      "Consistently single")
  # use tidy() for extraction
  broom::tidy(fit_obj, conf.int = TRUE, conf.level = 0.95) %>% 
    filter(label %in% c("a0", "a1", "cis", "bi", "bs", "vi", "vs")) %>% 
    mutate(outc = name_outc,
           group_fct = factor(group_lab, 
                            levels = c("Consistently single", "Consistently partnered", 
                                       "Intermittently partnered"), 
                            labels = c("Consistently single", "Consistently partnered", 
                                       "Intermittently partnered"), ordered = TRUE)) %>% 
    select(outc, group_fct, term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high,
           z_value = statistic, p_value = p.value, est_std = std.all)
}

# bind all model outputs together
rq2_summary_single <- bind_rows(
  extract_lav_rq2(fit_rq2_avoi_glo),
  extract_lav_rq2(fit_rq2_avoi_rom),
  extract_lav_rq2(fit_rq2_avoi_fri),
  extract_lav_rq2(fit_rq2_avoi_mot),
  extract_lav_rq2(fit_rq2_avoi_fat),
  extract_lav_rq2(fit_rq2_anxi_glo),
  extract_lav_rq2(fit_rq2_anxi_rom),
  extract_lav_rq2(fit_rq2_anxi_fri),
  extract_lav_rq2(fit_rq2_anxi_mot),
  extract_lav_rq2(fit_rq2_anxi_fat),
  extract_lav_rq2(fit_rq2_avoi_glo_partn_c),
  extract_lav_rq2(fit_rq2_avoi_rom_partn_c),
  extract_lav_rq2(fit_rq2_avoi_fri_partn_c),
  extract_lav_rq2(fit_rq2_avoi_mot_partn_c),
  extract_lav_rq2(fit_rq2_avoi_fat_partn_c),
  extract_lav_rq2(fit_rq2_anxi_glo_partn_c),
  extract_lav_rq2(fit_rq2_anxi_rom_partn_c),
  extract_lav_rq2(fit_rq2_anxi_fri_partn_c),
  extract_lav_rq2(fit_rq2_anxi_mot_partn_c),
  extract_lav_rq2(fit_rq2_anxi_fat_partn_c)
)

# Add labels
rq2_summary_single <- rq2_summary_single %>% 
  mutate(outc_fct = factor(outc, levels = outcomes$short, labels = outcomes$maj, ordered = TRUE))#

### multi-group lavaan models
# custom function for parameter extraction 
extract_lav_rq2_mg <- function(fit_obj, lrt_obj) {
  name_obj <- as.character(substitute(fit_obj))
  name_outc <- str_remove(name_obj, "fit_rq2_mg_")
  
  # extract LRT information
  lrt_tab <- as.data.frame(lrt_obj)
  lrt_chi <- lrt_tab$`Chisq diff`[2]
  lrt_df <- lrt_tab$`Df diff`[2]
  lrt_p <- lrt_tab$`Pr(>Chisq)`[2]
  
  # extract model parameters
  broom::tidy(fit_obj, conf.int = TRUE, conf.level = 0.95) %>% 
    filter(label %in% c("a0_s", "a0_p", "a1_s", "a1_p", "cis_s", "cis_p",
                        "bi_s", "bi_p", "bs_s", "bs_p", "vi_s", "vi_p", "vs_s", "vs_p")) %>% 
    mutate(outc = name_outc,
           group_fct = case_when(str_detect(label, "_s$") ~ "Consistently single",
                                 str_detect(label, "_p$") ~ "Consistently partnered",
                                 TRUE ~ NA_character_),
      group_fct = factor(group_fct, levels = c("Consistently single", "Consistently partnered",
                                    "Intermittently partnered"), ordered = TRUE),
      lrt_chi = ifelse(str_detect(label, "^a1_"), lrt_chi, NA),
      lrt_df = ifelse(str_detect(label, "^a1_"), lrt_df, NA),
      lrt_p = ifelse(str_detect(label, "^a1_"), lrt_p, NA)) %>% 
    select(outc, group_fct, term = label,
           est = estimate, ci_lo = conf.low, ci_hi = conf.high,
           z_value = statistic, p_value = p.value, est_std = std.all,
           lrt_chi, lrt_df, lrt_p)
}

# bind all model outputs together
rq2_summary_mg <- bind_rows(
  extract_lav_rq2_mg(fit_rq2_mg_avoi_glo, lrt_rq2_mg_avoi_glo),
  extract_lav_rq2_mg(fit_rq2_mg_avoi_rom, lrt_rq2_mg_avoi_rom),
  extract_lav_rq2_mg(fit_rq2_mg_avoi_fri, lrt_rq2_mg_avoi_fri),
  extract_lav_rq2_mg(fit_rq2_mg_avoi_mot, lrt_rq2_mg_avoi_mot),
  extract_lav_rq2_mg(fit_rq2_mg_avoi_fat, lrt_rq2_mg_avoi_fat),
  extract_lav_rq2_mg(fit_rq2_mg_anxi_glo, lrt_rq2_mg_anxi_glo),
  extract_lav_rq2_mg(fit_rq2_mg_anxi_rom, lrt_rq2_mg_anxi_rom),
  extract_lav_rq2_mg(fit_rq2_mg_anxi_fri, lrt_rq2_mg_anxi_fri),
  extract_lav_rq2_mg(fit_rq2_mg_anxi_mot, lrt_rq2_mg_anxi_mot),
  extract_lav_rq2_mg(fit_rq2_mg_anxi_fat, lrt_rq2_mg_anxi_fat)
)

# Add labels
rq2_summary_mg <- rq2_summary_mg %>% 
  mutate(outc_fct = factor(outc, levels = outcomes$short, labels = outcomes$maj, ordered = TRUE))
```

### Model fit

Fit statistics: single-group models
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

# model fit statistics: single-group models
rq2_fit_single <- outcomes$short %>% 
  purrr::map_dfr(function(x) {
    bind_rows(
      broom::glance(get(paste0("fit_rq2_", x))) %>% 
        mutate(outc = x, group_fct = "Consistently single"),
      broom::glance(get(paste0("fit_rq2_", x, "_partn_c"))) %>% 
        mutate(outc = x, group_fct = "Consistently partnered"))
  }) %>% 
  select(outc, group_fct, nobs, npar, AIC, BIC, cfi, rmsea, srmr) %>% 
  mutate(
    outc_fct = factor(outc, levels = outcomes$short, labels = outcomes$maj, ordered = TRUE),
    group_fct = factor(group_fct,
                       levels = c("Consistently single",
                                  "Consistently partnered",
                                  "Intermittently partnered"),
                       ordered = TRUE))

rq2_fit_single %>% select(-outc) %>% 
  select(outc_fct, group_fct, everything()) %>% 
  kable(digits = 3)
```

Fit statistics: multi-group models (of consistently single & consistently partnered)
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

# model fit statistics: multi-group models
rq2_fit_mg <- outcomes$short %>% 
  purrr::map_dfr(function(x) {
    broom::glance(get(paste0("fit_rq2_mg_", x))) %>% 
      mutate(outc = x)
  }) %>% 
  select(outc, nobs, npar, AIC, BIC, cfi, rmsea, srmr) %>% 
  mutate(outc_fct = factor(outc, levels = outcomes$short, labels = outcomes$maj, ordered = TRUE))

rq2_fit_mg %>% 
  select(-outc) %>% 
  select(outc_fct, everything()) %>% 
  kable(digits = 3)
```

### Model diagnostics

- Did the model converge?  
- Did lavaan's internal check pass?  
- Are there inadmissible negative variances?  

#### Single-group models

```{r}
#| echo: true
#| warning: true
#| output: true
#| cache: false
#| code-fold: true
#| code-summary: "Show the code"

# diagnostics for all single-group and partnered RQ2 models
rq2_models <- c("fit_rq2_avoi_glo", "fit_rq2_avoi_rom",
                "fit_rq2_avoi_fri", "fit_rq2_avoi_mot",
                "fit_rq2_avoi_fat", "fit_rq2_anxi_glo",
                "fit_rq2_anxi_rom", "fit_rq2_anxi_fri",
                "fit_rq2_anxi_mot", "fit_rq2_anxi_fat",
                "fit_rq2_avoi_glo_partn_c", "fit_rq2_avoi_rom_partn_c",
                "fit_rq2_avoi_fri_partn_c", "fit_rq2_avoi_mot_partn_c",
                "fit_rq2_avoi_fat_partn_c", "fit_rq2_anxi_glo_partn_c",
                "fit_rq2_anxi_rom_partn_c", "fit_rq2_anxi_fri_partn_c",
                "fit_rq2_anxi_mot_partn_c", "fit_rq2_anxi_fat_partn_c")

rq2_diagnostics <- purrr::map_dfr(rq2_models, function(x) {
  fit <- get(x)
  tibble(
    model = x,
    converged = lavInspect(fit, "converged"),
    post_check = lavInspect(fit, "post.check"),
    neg_variances = any(parameterEstimates(fit)$op == "~~" &
                          parameterEstimates(fit)$lhs == parameterEstimates(fit)$rhs &
                          parameterEstimates(fit)$est < 0))
})

rq2_diagnostics %>% kable(digits = 3)
```

#### Multi-group models

```{r}
#| echo: true
#| warning: true
#| output: true
#| cache: false
#| code-fold: true
#| code-summary: "Show the code"

rq2_mg_models <- c("fit_rq2_mg_avoi_glo", "fit_rq2_mg_avoi_rom",
                   "fit_rq2_mg_avoi_fri", "fit_rq2_mg_avoi_mot",
                   "fit_rq2_mg_avoi_fat", "fit_rq2_mg_anxi_glo",
                   "fit_rq2_mg_anxi_rom", "fit_rq2_mg_anxi_fri",
                   "fit_rq2_mg_anxi_mot", "fit_rq2_mg_anxi_fat")

rq2_mg_diagnostics <- purrr::map_dfr(rq2_mg_models, function(x) {
  fit <- get(x)
  pe <- parameterEstimates(fit)
  tibble(
    model = x,
    converged = lavInspect(fit, "converged"),
    post_check = lavInspect(fit, "post.check"),
    neg_variances = any(pe$op == "~~" &
                          pe$lhs == pe$rhs &
                          pe$est < 0))
})

rq2_mg_diagnostics %>% kable(digits = 3)
```

### Summary tables

#### Single-group models

Latent intercept and slope factors: "alpha0" (a0) & "alpha1" (a1): 

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq2_table_a <- rq2_summary_single %>% 
  filter(term=="a0" | term=="a1") %>%
  arrange(outc_fct, group_fct, term) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq2_table_a %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 4, length.out = nrow(rq2_table_a))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Very similar .
:::

Latent intercept-slope covariance: (cis) 

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq2_table_cis <- rq2_summary_single %>% 
  filter(term=="cis") %>% 
  arrange(outc_fct, group_fct) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq2_table_cis %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 2, length.out = nrow(rq2_table_cis))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Significant ...
:::

Variances of the latent intercept and slope factors: (vi) & (vs)

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq2_table_v <- rq2_summary_single %>% 
  filter(stringr::str_starts(term, "v")) %>% 
  arrange(outc_fct, group_fct, term) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq2_table_v %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 4, length.out = nrow(rq2_table_v))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Significant ...
:::

Age moderation of latent intercept and slope factors: (bi) & (bs)

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq2_table_b <- rq2_summary_single %>% 
  filter(term=="bi" | term=="bs") %>% 
  arrange(outc_fct, group_fct, term) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq2_table_b %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 4, length.out = nrow(rq2_table_b))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Significant ...
:::

#### Multi-group models

Latent intercept and slope factors: "alpha0" (a0) & "alpha1" (a1)  

--> "_s" for single, "_p" for partnered  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq2_table_mg_a <- rq2_summary_mg %>% 
  filter(stringr::str_starts(term, "a")) %>%
  arrange(outc_fct, group_fct, term) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value, lrt_chi, lrt_p)

rq2_table_mg_a %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 4, length.out = nrow(rq2_table_mg_a))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Very similar .
:::

Latent intercept-slope covariance: (cis)  

--> "_s" for single, "_p" for partnered  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq2_table_mg_cis <- rq2_summary_mg %>% 
  filter(stringr::str_starts(term, "cis")) %>% 
  arrange(outc_fct, group_fct, term) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq2_table_mg_cis %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 2, length.out = nrow(rq2_table_mg_cis))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Significant ...
:::

Variances of the latent intercept and slope factors: (vi) & (vs)  

--> "_s" for single, "_p" for partnered  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq2_table_mg_v <- rq2_summary_mg %>% 
  filter(stringr::str_starts(term, "v")) %>% 
  arrange(outc_fct, group_fct, term) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq2_table_mg_v %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 4, length.out = nrow(rq2_table_mg_v))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Significant ...
:::

Age moderation of latent intercept and slope factors: (bi) & (bs)  

--> "_s" for single, "_p" for partnered  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq2_table_mg_b <- rq2_summary_mg %>% 
  filter(stringr::str_starts(term, "b")) %>% 
  arrange(outc_fct, group_fct, term) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq2_table_mg_b %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 4, length.out = nrow(rq2_table_mg_b))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Significant ...
:::


### Summary plot

Create plots for manuscript: start with extracting the parameters

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

# Custom function to extract model-implied trajectories from lavaan defined parameters
extract_rq2_plot_traject <- function(fit, outcome_label) {
  parameterEstimates(fit, ci = TRUE) %>%
    as_tibble() %>%
    filter(op == ":=") %>%
    mutate(group = case_when(str_detect(lhs, "_s$") ~ "Consistently single",
                             str_detect(lhs, "_p$") ~ "Consistently partnered"),
           month = as.numeric(str_extract(lhs, "(?<=t)\\d+")),
           time_years = month / 12,
           outcome = outcome_label) %>%
    select(outcome, group, month, time_years, estimate = est, ci_low = ci.lower, ci_high = ci.upper)
}

# Extract trajectories from all multi-group RQ2 models
plot_traject_list_rq2 <- list()
for (i in 1:length(outcomes$short)) {
  fit <- readRDS(paste0("models/fit_rq2_mg_", outcomes$short[i], ".rds"))
  plot_traject_list_rq2[[i]] <- extract_rq2_plot_traject(fit, outcomes$maj[i])
}
plot_traject_df_rq2 <- bind_rows(plot_traject_list_rq2)

# Check extracted plotting dataframe
head(plot_traject_df_rq2)
table(plot_traject_df_rq2$outcome, plot_traject_df_rq2$group)

# create factor variables:
plot_traject_df_rq2 <- plot_traject_df_rq2 %>%
  mutate(outc_fct = factor(outcome, levels = outcomes$maj, labels = outcomes$maj, ordered = TRUE),
         group_fct = factor(group, levels = c("Consistently single", "Consistently partnered"), ordered = TRUE))

# a bit tricky: handling variable y-axis ranges...
# Define common y-axis width across facets
y_range_rq2 <- 1.7
# Calculate facet-specific y-axis limits with equal zoom
plot_traject_limits_rq2 <- plot_traject_df_rq2 %>%
  group_by(outc_fct) %>%
  summarise(y_mid = mean(range(c(ci_low, ci_high)))) %>%
  mutate(y_lower = y_mid - y_range_rq2 / 2,
         y_upper = y_mid + y_range_rq2 / 2)
# Create facet-specific y-axis scales with half-point breaks
y_scales_rq2 <- lapply(1:nrow(plot_traject_limits_rq2), function(i) {
  scale_y_continuous(limits = c(plot_traject_limits_rq2$y_lower[i],
                                plot_traject_limits_rq2$y_upper[i]),
                     breaks = seq(floor(plot_traject_limits_rq2$y_lower[i] * 2) / 2,
                                  ceiling(plot_traject_limits_rq2$y_upper[i] * 2) / 2,
                                  by = 0.5),
                     labels = scales::label_number(accuracy = 0.1))
})

# Create significance labels from LRT p-values
rq2_sig_labels <- rq2_table_mg_a %>%
  filter(term == "a1_s") %>%
  mutate(sig = case_when(lrt_p < .001 ~ "***",
                         lrt_p < .01 ~ "**",
                         lrt_p < .05 ~ "*",
                         TRUE ~ "")) %>%
  select(outc_fct, sig) %>% 
  mutate(outc_label = ifelse(sig == "", as.character(outc_fct), paste0(as.character(outc_fct), " (", sig, ")")))
# Add labelled outcome factor for plotting
plot_traject_df_rq2 <- plot_traject_df_rq2 %>%
  left_join(rq2_sig_labels %>% select(outc_fct, outc_label), by = "outc_fct") %>%
  mutate(outc_fct_label = factor(outc_label, levels = unique(outc_label))) %>% 
  mutate(outc_fct_label = factor(outc_fct_label, levels = unique(outc_fct_label), ordered = TRUE))
```

Creat and save plot: 
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false
#| code-fold: true
#| code-summary: "Show the code"

# Define custom group colours
group_colors <- c("Consistently single" = "steelblue4", "Consistently partnered" = "darkorange2")

# Plot RQ2 model-implied trajectories with 95% confidence bands
plot_rq2_traject <- ggplot(plot_traject_df_rq2, aes(x = time_years, y = estimate, 
                                                     colour = group_fct, fill = group_fct)) +
  geom_ribbon(aes(ymin = ci_low, ymax = ci_high), alpha = .20, colour = NA) +
  geom_line(linewidth = 1) +
  scale_colour_manual(values = group_colors) +
  scale_fill_manual(values = group_colors) +
  facet_wrap(~outc_fct_label, ncol = 2, nrow = 5, scales = "free_y", dir = "v") +
  ggh4x::facetted_pos_scales(y = y_scales_rq2) +
  labs(x = "Years since baseline", y = "Attachment domain (model-implied; 95% CI-band)", colour = NULL, fill = NULL) +
  guides(colour = guide_legend(title = "Group"),
         fill = guide_legend(title = "Group")) +
  theme_bw() +
  theme(strip.text = element_text(size = 10),
        strip.background = element_rect(fill = "grey95"),
        legend.position = "bottom",
        legend.key.width = unit(1.3, "cm"),
        panel.grid.major.y = element_line(color = "grey80", linewidth = 0.3),
        panel.grid.minor.y = element_blank(),
        panel.grid.major.x = element_blank(),
        panel.grid.minor.x = element_blank())

plot_rq2_traject

# save as pdf
pdf(width = 6.5, height = 7.5, "figures/rq2_traject.pdf")
plot_rq2_traject
dev.off()
```

Show plot: 
```{r rq2-summary-plot-show}
#| echo: true
#| fig-width: 6.5
#| fig-height: 7.5
#| cache: false

plot_rq2_traject
```

### Full model results

#### Single-group models

##### `r outcomes$maj[1]`

Full model results for `r outcomes$min[1]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[1])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

Full model results for `r outcomes$min[1]` (in the consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[1], "_partn_c")), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[2]`

Full model results for `r outcomes$min[2]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[2])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

Full model results for `r outcomes$min[2]` (in the consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[2], "_partn_c")), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[3]`

Full model results for `r outcomes$min[3]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[3])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

Full model results for `r outcomes$min[3]` (in the consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[3], "_partn_c")), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[4]`

Full model results for `r outcomes$min[4]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[4])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

Full model results for `r outcomes$min[4]` (in the consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[4], "_partn_c")), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[5]`

Full model results for `r outcomes$min[5]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[5])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

Full model results for `r outcomes$min[5]` (in the consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[5], "_partn_c")), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[6]`

Full model results for `r outcomes$min[6]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[6])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

Full model results for `r outcomes$min[6]` (in the consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[6], "_partn_c")), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[7]`

Full model results for `r outcomes$min[7]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[7])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

Full model results for `r outcomes$min[7]` (in the consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[7], "_partn_c")), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[8]`

Full model results for `r outcomes$min[8]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[8])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

Full model results for `r outcomes$min[8]` (in the consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[8], "_partn_c")), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[9]`

Full model results for `r outcomes$min[9]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[9])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

Full model results for `r outcomes$min[9]` (in the consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[9], "_partn_c")), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[10]`

Full model results for `r outcomes$min[10]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[10])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

Full model results for `r outcomes$min[10]` (in the consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_", outcomes$short[10], "_partn_c")), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

#### Multi-group models

##### `r outcomes$maj[1]`

Full model results for `r outcomes$min[1]` (comparing consistently single & consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_mg_", outcomes$short[1])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[2]`

Full model results for `r outcomes$min[2]` (comparing consistently single & consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_mg_", outcomes$short[2])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[3]`

Full model results for `r outcomes$min[3]` (comparing consistently single & consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_mg_", outcomes$short[3])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[4]`

Full model results for `r outcomes$min[4]` (comparing consistently single & consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_mg_", outcomes$short[4])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[5]`

Full model results for `r outcomes$min[5]` (comparing consistently single & consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_mg_", outcomes$short[5])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[6]`

Full model results for `r outcomes$min[6]` (comparing consistently single & consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_mg_", outcomes$short[6])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[7]`

Full model results for `r outcomes$min[7]` (comparing consistently single & consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_mg_", outcomes$short[7])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[8]`

Full model results for `r outcomes$min[8]` (comparing consistently single & consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_mg_", outcomes$short[8])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[9]`

Full model results for `r outcomes$min[9]` (comparing consistently single & consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_mg_", outcomes$short[9])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



##### `r outcomes$maj[10]`

Full model results for `r outcomes$min[10]` (comparing consistently single & consistently partnered people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq2_mg_", outcomes$short[10])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```

## RQ3: Co-Development of Attachment and Life Satisfaction

From prereg: "To examine co-development, we will estimate bivariate latent growth curve models of attachment and life satisfaction within the group of consistently single people, as well as exploratorily in the each of the partnered groups. These will build progressively on the univariate models (RQ2), adding life satisfaction as the second construct."  

"The main effects of interest are the cross-construct intercept-slope correlations and slope-slope correlations. Again, we will run separate models for the different attachment variables (2 x 5 models in each group)."  

I'm doing the main models for all attachment domains in this section (in single people), even though we only investigate global and friend-specific as confirmatory and the rest as exploratory. However, the exploration of consistently partnered people and intermittently partnered individuals will follow below in the next section.  

### Example model

I'm first creating a template and show this with an example model of global avoidance (in single people). Below, I loop through all outcomes using the template.  

Specify model template, and show example model output:   

("a" is generally for attachment in this code, and "w" for well-being = life satisfaction)  
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true

# bivariate latent growth curve model: single-group

# Define number of assessment waves
n_waves <- 30  # t00 to t29

# Create variable names
times <- sprintf("%02d", 0:(n_waves - 1))
outcome_vars <- paste0("outcome_t", times)
swb_vars <- paste0("swb_t", times)

# Intercept loadings
i_loadings_out <- paste0("1*", outcome_vars, collapse = " + ")
i_loadings_swb <- paste0("1*", swb_vars, collapse = " + ")

# Slope loadings (scaled 0 to 1)
s_values <- seq(0, 1, length.out = n_waves)
s_loadings_out <- paste0(round(s_values, 5), "*", outcome_vars, collapse = " + ")
s_loadings_swb <- paste0(round(s_values, 5), "*", swb_vars, collapse = " + ")

# Residual variance labels
res_out <- paste0(outcome_vars, " ~~ ra", times, "*", outcome_vars, collapse = "\n")
res_swb <- paste0(swb_vars, " ~~ rw", times, "*", swb_vars, collapse = "\n")

# Residual covariance labels
res_cov <- paste0(outcome_vars, " ~~ rc", times, "*", swb_vars, collapse = "\n")

# Bivariate LGCM template
rq3_template <- paste0('
# Define intercept and slope factors
ia =~ ', i_loadings_out, '
sa =~ ', s_loadings_out, '

iw =~ ', i_loadings_swb, '
sw =~ ', s_loadings_swb, '

# Regress latent growth factors on baseline age
ia ~ bia*age_base_z
sa ~ bsa*age_base_z
iw ~ biw*age_base_z
sw ~ bsw*age_base_z

# Mean structure
ia ~ a0*1
sa ~ a1*1
iw ~ w0*1
sw ~ w1*1

# Variance structure
ia ~~ via*ia
sa ~~ vsa*sa
ia ~~ cisa*sa

iw ~~ viw*iw
sw ~~ vsw*sw
iw ~~ cisw*sw

# Cross-process covariances
ia ~~ cii*iw
ia ~~ cis_aw*sw
iw ~~ cis_wa*sa
sa ~~ css*sw

# Residual variances
', res_out, '

', res_swb, '

# Residual covariances
', res_cov, '
')

# Example model with global avoidance
model_rq3_avoi_glo_example <- stringr::str_replace_all(rq3_template, "outcome", "avoi_glo")

# Fit model
fit_rq3_avoi_glo_example <- lavaan::growth(model_rq3_avoi_glo_example,
                                           data = df_atta_wide_single_c,
                                           missing = "fiml", verbose = FALSE)

summary(fit_rq3_avoi_glo_example, fit.measures = TRUE, standardized = TRUE, ci = FALSE)
```

::: {.callout-note appearance="minimal"}
Global avoidance decreases ...  

I also tried out an otherwise identical model without residual covariances but fit was worse, supporting the retention of the residual covariance structure. But mostly these residual covariances also make sense from a theoretical standpoint because they account for occasion-specific shared influences not captured by the latent trajectories.   
:::

### Template loop

Run loop over all 5 X 2 outcomes  

(Here, I suppress lavaan warnings in the html output, but they are very similar to the ones shown above for the example model. Below, I go into model diagnostics more systematically.)  

```{r rq3-loop}
#| echo: true
#| warning: false
#| output: false
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

# loop across all attachment outcomes
for (i in 1:length(outcomes$short)) {
  print(paste0("Running outcome: ", outcomes$maj[i]))

  # Fill bivariate LGCM template
  model_rq3 <- stringr::str_replace_all(rq3_template, "outcome", outcomes$short[i])

  # Fit model in consistently single people
  fit_rq3 <- lavaan::growth(model_rq3,
                            data = df_atta_wide_single_c,
                            missing = "fiml",
                            verbose = FALSE)

  # Save model object
  eval(call("<-", as.name(paste0("fit_rq3_", outcomes$short[i])), fit_rq3))
  saveRDS(fit_rq3, file = paste0("models/fit_rq3_", outcomes$short[i], ".rds"))
}
```

Create summary table of all effects of interest:  

First, parameter extraction  
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

# custom function for parameter extraction from bivariate LGCMs
extract_lav_rq3 <- function(fit_obj) {
  name_obj <- as.character(substitute(fit_obj))
  name_outc <- name_obj %>% 
    str_remove("fit_rq3_") %>% 
    str_remove("_partn_c$|_partn_i$")
  group_lab <- case_when(str_detect(name_obj, "_partn_c$") ~ "Consistently partnered",
                         str_detect(name_obj, "_partn_i$") ~ "Intermittently partnered",
                         TRUE ~ "Consistently single")
  # filter parameters of interest
  broom::tidy(fit_obj, conf.int = TRUE, conf.level = 0.95) %>% 
    filter(label %in% c("a0", "a1", "w0", "w1",
                        "bia", "bsa", "biw", "bsw",
                        "via", "vsa", "cisa",
                        "viw", "vsw", "cisw",
                        "cii", "cis_aw", "cis_wa", "css")) %>% 
    mutate(outc = name_outc,
           group_fct = factor(group_lab, levels = c("Consistently single", "Consistently partnered",
                                                    "Intermittently partnered"),
                              ordered = TRUE)) %>% 
    select(outc, group_fct, term = label,
           est = estimate, ci_lo = conf.low, ci_hi = conf.high,
           z_value = statistic, p_value = p.value,
           est_std = std.all)
}

# bind all model outputs together
rq3_summary <- bind_rows(
  extract_lav_rq3(fit_rq3_avoi_glo),
  extract_lav_rq3(fit_rq3_avoi_rom),
  extract_lav_rq3(fit_rq3_avoi_fri),
  extract_lav_rq3(fit_rq3_avoi_mot),
  extract_lav_rq3(fit_rq3_avoi_fat),
  extract_lav_rq3(fit_rq3_anxi_glo),
  extract_lav_rq3(fit_rq3_anxi_rom),
  extract_lav_rq3(fit_rq3_anxi_fri),
  extract_lav_rq3(fit_rq3_anxi_mot),
  extract_lav_rq3(fit_rq3_anxi_fat)
)
# Add labels
rq3_summary <- rq3_summary %>% 
  mutate(outc_fct = factor(outc, levels = outcomes$short,
                           labels = outcomes$maj, ordered = TRUE))
```

### Model fit

Fit statistics: 
```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

# model fit statistics: single-group models
rq3_fit_single <- outcomes$short %>% 
  purrr::map_dfr(function(x) {
    bind_rows(
      broom::glance(get(paste0("fit_rq3_", x))) %>% 
        mutate(outc = x, group_fct = "Consistently single"))
  }) %>% 
  select(outc, group_fct, nobs, npar, AIC, BIC, cfi, rmsea, srmr) %>% 
  mutate(
    outc_fct = factor(outc, levels = outcomes$short, labels = outcomes$maj, ordered = TRUE),
    group_fct = factor(group_fct,
                       levels = c("Consistently single",
                                  "Consistently partnered",
                                  "Intermittently partnered"),
                       ordered = TRUE))

rq3_fit_single %>% select(-outc) %>% 
  select(outc_fct, group_fct, everything()) %>% 
  kable(digits = 3)
```

::: {.callout-note appearance="minimal"}
Pretty similar across outcomes, with the exception of Avoidance: Best Friend. Here, the latent slope variance is considerably larger than in the global model. This means friend-avoidance has much more heterogeneous trajectories and a single linear slope will fit relatively poorly. Other than that, there is no indication for "technical" issues with this model or implausible estimates. Occasion-specific variation (in the residuals) is also quite large here. Another explanation could be nonlinear change. However, in the observed means, a linear slope looks like a very reasonable approximation of the trajectory (descriptively).   
:::

### Model diagnostics

- Did the model converge?  
- Did lavaan's internal check pass?  
- Are there inadmissible negative variances?  

```{r}
#| echo: true
#| warning: true
#| output: true
#| cache: false
#| code-fold: true
#| code-summary: "Show the code"

# diagnostics for all single-group and partnered RQ2 models
rq3_models <- c("fit_rq3_avoi_glo", "fit_rq3_avoi_rom",
                "fit_rq3_avoi_fri", "fit_rq3_avoi_mot",
                "fit_rq3_avoi_fat", "fit_rq3_anxi_glo",
                "fit_rq3_anxi_rom", "fit_rq3_anxi_fri",
                "fit_rq3_anxi_mot", "fit_rq3_anxi_fat")

rq3_diagnostics <- purrr::map_dfr(rq3_models, function(x) {
  fit <- get(x)
  tibble(
    model = x,
    converged = lavInspect(fit, "converged"),
    post_check = lavInspect(fit, "post.check"),
    neg_variances = any(parameterEstimates(fit)$op == "~~" &
                          parameterEstimates(fit)$lhs == parameterEstimates(fit)$rhs &
                          parameterEstimates(fit)$est < 0))
})

rq3_diagnostics %>% kable(digits = 3)
```

### Summary tables

Latent intercept and slope factors: "alpha0" (a0 = attach, w0 = life sat) & "alpha1" (a1 = attach, w1 = life sat): 

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq3_table_a <- rq3_summary %>% 
  filter(term=="a0" | term=="a1" | term=="w0" | term=="w1") %>% 
  arrange(outc_fct, group_fct, term) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq3_table_a %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 4, length.out = nrow(rq3_table_a))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Very similar .
:::

Latent intercept / slope variances & covariance - general terminology:  
- (a) = attachment  
- (w) = well-being (life satisf.)  
- (c) = covariance  
- (v) = variance  
- (i) = latent intercept  
- (s) = latent slope   

First, cross-construct covariances (which are most relevant for the hypotheses):  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq3_table_cross <- rq3_summary %>% 
  filter(term %in% c("cii", "cis_aw", "cis_wa", "css")) %>% 
  arrange(outc_fct, group_fct) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq3_table_cross %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 4, length.out = nrow(rq3_table_cross))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Significant ...
:::

First, within-construct intercept-slope covariances:  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq3_table_cis <- rq3_summary %>% 
  filter(term %in% c("cisa", "cisw")) %>% 
  arrange(outc_fct, group_fct) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq3_table_cis %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 2, length.out = nrow(rq3_table_cis))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Significant ...
:::

Variances of the latent intercept and slope factors: (via, viw) & (vis, vws)  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq3_table_v <- rq3_summary %>% 
  filter(stringr::str_starts(term, "v")) %>% 
  arrange(outc_fct, group_fct, term) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq3_table_v %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 4, length.out = nrow(rq3_table_v))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Significant ...
:::

Age moderation of latent intercept and slope factors: (bi) & (bs)

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

rq3_table_b <- rq3_summary %>% 
  filter(stringr::str_starts(term, "bi") | stringr::str_starts(term, "bs")) %>% 
  arrange(outc_fct, group_fct, term) %>% 
  select(outc_fct, group_fct, term, est, ci_lo, ci_hi, p_value)

rq3_table_b %>% 
  knitr::kable(digits = 3, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, bootstrap_options = c("bordered")) %>% 
  kableExtra::row_spec(which(rep(c(TRUE, FALSE), each = 4, length.out = nrow(rq3_table_b))),
                       background = "lightgrey")
```

::: {.callout-note appearance="minimal"}
Significant ...
:::


### Summary plot

Plot for main manuscript: focusing on confirmatory analyses  

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: false
#| code-fold: true
#| code-summary: "Show the code"

# for alternating background greys

# save as pdf
# pdf(width = 5, height = 4.5, "figures/effects_summary_rq3.pdf")
# plot_rq3
# dev.off()
```

Show plot: 
```{r rq3-summary-plot-show}
#| echo: true
#| fig-width: 5
#| fig-height: 4.5
#| cache: false

#plot_rq3
```

### Full model results

#### `r outcomes$maj[1]`

Full model results for `r outcomes$min[1]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq3_", outcomes$short[1])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



#### `r outcomes$maj[2]`

Full model results for `r outcomes$min[2]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq3_", outcomes$short[2])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



#### `r outcomes$maj[3]`

Full model results for `r outcomes$min[3]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq3_", outcomes$short[3])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



#### `r outcomes$maj[4]`

Full model results for `r outcomes$min[4]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq3_", outcomes$short[4])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



#### `r outcomes$maj[5]`

Full model results for `r outcomes$min[5]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq3_", outcomes$short[5])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



#### `r outcomes$maj[6]`

Full model results for `r outcomes$min[6]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq3_", outcomes$short[6])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



#### `r outcomes$maj[7]`

Full model results for `r outcomes$min[7]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq3_", outcomes$short[7])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



#### `r outcomes$maj[8]`

Full model results for `r outcomes$min[8]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq3_", outcomes$short[8])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



#### `r outcomes$maj[9]`

Full model results for `r outcomes$min[9]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq3_", outcomes$short[9])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



#### `r outcomes$maj[10]`

Full model results for `r outcomes$min[10]` (in the consistently single people):

```{r}
#| echo: true
#| warning: false
#| output: true
#| cache: true
#| code-fold: true
#| code-summary: "Show the code"

broom::tidy(get(paste0("fit_rq3_", outcomes$short[10])), conf.int = TRUE, conf.level = 0.95) %>% 
  filter(label != "") %>% 
  arrange(label) %>% 
  select(term = label, est = estimate, ci_lo = conf.low, ci_hi = conf.high, p_value = p.value, est_std = std.all) %>% 
  knitr::kable(digits = 3)
```



# Exploratory analyses

## RQ2: Changes in Attachment Models

From prereg: "For all attachment models, we will also explore whether consistently single people experience differential changes in attachment compared to intermittently partnered individuals."  

Same procedure as above: We 

## RQ3: Co-Development of Attachment and Life Satisfaction

From prereg: "In addition, for all attachment models, we will explore co-development between attachment and life satisfaction in (1) consistently partnered individuals and (2) intermittently partnered individuals."

::: {.callout-note appearance="minimal"}
The p-value is not significant ...   
:::

# Robustness checks

## LGCM re-run as multilevel models

## LGCM but only up to 24 months 

# Packages used

```{r pkgs}
pkgs <- grateful::cite_packages(output = "table", out.dir = ".")
knitr::kable(pkgs)
```
